---
title: "Sensitivity, Specificity, and Feature Importance for ML Classification of siRNA Depletion Data"
output: html_notebook
---
This code compiles cleaned and scaled feature data for the siRNA depletion experiments, and applies the ML classifier generated in the siRNA_MachineLearning.Rmd notebook.

It calculates the sensitivity and specificity of each iteration of training and for the final classifier (Fig. 5D, Supp. Fig. 7A). It also examines feature importance and generates violin plots for the most important features. It generates the violin plot of feature values based on manual scoring (Fig. 5B).

Supplemental data for Supp. Table S13 in the last chunks.

```{r}
dirPath <- "/Your/Directory/Path/"
```

Load packages:
```{r}
options(java.parameters = "-Xmx8g")
library(readxl)
library(tidyverse)
library(caret)
library(gridExtra)
# options(rgl.useNULL=TRUE)
# library(rgl)
# library(Rdimtools)
library(gbm)
library(extraTrees)
library(ggbeeswarm)

```
Functions
```{r}
# This function accepts Matlab output for 2- or 3-channel experiments, and combines them into one data.frame, appending the variable names of the channel specific measurements with the channel name provided in the input (e.g., the name of the stained protein). For a 3-channel experiment Matlab exports 4 files. The _Cell file contains colocalization metrics and measurements shared by all channels (i.e., Area, Max Feret Diameter, etc.). The other files (_chName) contain channel specific measurements. Provide the full path for the matlab files in the function input.
importMatlabMulti <- function(matlabCell, matlabChannel1, matlabChannel2, matlabChannel3, annotationdf, ch1Name, ch2Name, ch3Name){
  cellMeasRaw <- read.csv(matlabCell)
  cellMeas <- cellMeasRaw %>%
    filter(!cell == "")
  cellMeas <- unique(cellMeas)
  
  ch1 <- unique(cbind(cellMeasRaw %>% dplyr::select(Area, cell), read.csv(matlabChannel1))) %>%
    filter(!is.na(intensityWrampHalves)) %>%
    dplyr::rename(meanIntensityNotWramp = meanNotWramp,
           medianIntensityNotWramp = medianNotWramp,
           sumIntensityNotWramp = sumNotWramp,
           meanIntensityNotBright = meanNotBright,
           sumIntensityNotBright = sumNotBright,
           medianIntensityNotBright = medianNotBright) %>%
    dplyr::mutate(meanWrampOverNot = meanIntensityWramp/meanIntensityNotWramp,
           meanWrampOverNotBright = meanIntensityWramp/meanIntensityNotBright,
           meanSecondOverNotBright = meanIntensitySecond/meanIntensityNotBright,
           sumWrampOverNot = sumIntensityWramp/sumIntensityNotWramp,
           sumWrampOverNotBright = sumIntensityWramp/sumIntensityNotBright,
           sumSecondOverNotBright = sumIntensitySecond/sumIntensityNotBright,
           medianWrampOverNot = medianIntensityWramp/medianIntensityNotWramp,
           medianWrampOverNotBright = medianIntensityWramp/medianIntensityNotBright,
           medianSecondOverNotBright = medianIntensitySecond/medianIntensityNotBright,
           sumOverMedianIntensityWramp = sumIntensityWramp/medianIntensityWramp,
           relAreaWrampCell = areaWramp/Area,
           relAreaWrampBright = areaWramp/areaBrightObj,
           massDisplacement = ifelse(massDisplacement < 1, 1, massDisplacement)) %>%
    dplyr::select(-Area) %>%
    rename_with(~str_c(.,paste("_", ch1Name, sep = "")), .cols = -contains("cell", ignore.case = F))
  ch2 <- unique(cbind(read.csv(matlabChannel2), cellMeasRaw %>% dplyr::select(Area, cell))) %>%
    filter(cell %in% ch1$cell) %>%
    dplyr::rename(meanIntensityNotWramp = meanNotWramp,
           medianIntensityNotWramp = medianNotWramp,
           sumIntensityNotWramp = sumNotWramp,
           meanIntensityNotBright = meanNotBright,
           sumIntensityNotBright = sumNotBright,
           medianIntensityNotBright = medianNotBright) %>%
    dplyr::mutate(meanWrampOverNot = meanIntensityWramp/meanIntensityNotWramp,
           meanWrampOverNotBright = meanIntensityWramp/meanIntensityNotBright,
           meanSecondOverNotBright = meanIntensitySecond/meanIntensityNotBright,
           sumWrampOverNot = sumIntensityWramp/sumIntensityNotWramp,
           sumWrampOverNotBright = sumIntensityWramp/sumIntensityNotBright,
           sumSecondOverNotBright = sumIntensitySecond/sumIntensityNotBright,
           medianWrampOverNot = medianIntensityWramp/medianIntensityNotWramp,
           medianWrampOverNotBright = medianIntensityWramp/medianIntensityNotBright,
           medianSecondOverNotBright = medianIntensitySecond/medianIntensityNotBright,
           sumOverMedianIntensityWramp = sumIntensityWramp/medianIntensityWramp,
           relAreaWrampCell = areaWramp/Area,
           relAreaWrampBright = areaWramp/areaBrightObj,
           massDisplacement = ifelse(massDisplacement < 1, 1, massDisplacement)) %>%
        dplyr::select(-Area) %>%
    rename_with(~str_c(.,paste("_", ch2Name, sep = "")), .cols = -contains("cell", ignore.case = F))
  if(matlabChannel3 != "empty"){
    ch3 <- unique(cbind(cellMeasRaw %>% dplyr::select(Area, cell), read.csv(matlabChannel3))) %>%
      filter(cell %in% ch1$cell) %>%
      dplyr::rename(meanIntensityNotWramp = meanNotWramp,
             medianIntensityNotWramp = medianNotWramp,
             sumIntensityNotWramp = sumNotWramp,
             meanIntensityNotBright = meanNotBright,
             sumIntensityNotBright = sumNotBright,
             medianIntensityNotBright = medianNotBright) %>%
      dplyr::mutate(meanWrampOverNot = meanIntensityWramp/meanIntensityNotWramp,
             meanWrampOverNotBright = meanIntensityWramp/meanIntensityNotBright,
             meanSecondOverNotBright = meanIntensitySecond/meanIntensityNotBright,
             sumWrampOverNot = sumIntensityWramp/sumIntensityNotWramp,
             sumWrampOverNotBright = sumIntensityWramp/sumIntensityNotBright,
             sumSecondOverNotBright = sumIntensitySecond/sumIntensityNotBright,
             medianWrampOverNot = medianIntensityWramp/medianIntensityNotWramp,
             medianWrampOverNotBright = medianIntensityWramp/medianIntensityNotBright,
             medianSecondOverNotBright = medianIntensitySecond/medianIntensityNotBright,
             sumOverMedianIntensityWramp = sumIntensityWramp/medianIntensityWramp,
             relAreaWrampCell = areaWramp/Area,
             relAreaWrampBright = areaWramp/areaBrightObj,
             massDisplacement = ifelse(massDisplacement < 1, 1, massDisplacement)) %>%
      dplyr::select(-Area) %>%
      rename_with(~str_c(.,paste("_", ch3Name, sep = "")), .cols = -contains("cell", ignore.case = F))
  }
  
  if(matlabChannel3 != "empty"){
    matlab <- merge(cellMeas, merge(ch1, merge(ch2, ch3, by = "cell"), by = "cell"), by = "cell")
  }else{
    matlab <- merge(cellMeas, merge(ch1, ch2, by = "cell"), by = "cell")
  }
  matlab <- matlab %>%
    separate(cell, into = c("Image", "ObjectNumber"), sep = "Cell_", convert = TRUE) %>%
    dplyr::select(-Image) %>%
    dplyr::rename(Image = image) %>%
    #filter(!is.na(ObjectNumber)) %>%
    unite(Object, c("Image","ObjectNumber"), remove = FALSE) %>%
    dplyr::select(-ObjectNumber) %>%
    arrange(Object)
    
  
  matlabAnnotated <- merge(annotationdf, matlab, by = "Image")
}

# This function reads cell-level results from CellProfiler and adds annotation from the image file
readCp <- function(cpImgPath, cpCellPath){
  cpImg <-read.csv(cpImgPath)
  
  if(any(str_detect(colnames(cpImg), "Image_FileName_ImgMcam"))){
    cpCell <- merge(read.csv(cpCellPath), dplyr::select(cpImg, ImageNumber, Image_FileName_ImgMcam), by = "ImageNumber") %>%
      unite(Object, c(Image_FileName_ImgMcam, ObjectNumber), remove = F) %>%
      arrange(Object)
  }else{
    cpCell <- merge(read.csv(cpCellPath), dplyr::select(cpImg, ImageNumber, Image_FileName_ImgMain), by = "ImageNumber") %>%
      unite(Object, c(Image_FileName_ImgMain, ObjectNumber), remove = F) %>%
      arrange(Object)
  }
}

# This function combines features measured in matlab and CellProfiler, removes redundant features, calculates CV for Intensity and IntensityEdge from CellProfiler measurements, converts Haralick features into rotation-invariant form (not angularly dependent) by taking the mean and range, and removes small round cells based on area and max Feret diameter. CellProfiler subscript (cpSubscript) and matlab channel names (chName) indicating the different channels need to match the subscripts in the input dataframes.
combineMetrics <- function(matlab, cpCell, cpSubscript1, cpSubscript2, cpSubscript3, chName1, chName2, chName3){
  metrics <- merge(matlab, cpCell, by = "Object") %>%
    dplyr::select(-AreaShape_Orientation, 
           -contains("Intensity_MedianIntensity_BgSubtracted"), 
           -contains("Intensity_IntegratedIntensity"),
           -contains("Intensity_MassDisplacement"),
           -Number_Object_Number,
           -AreaShape_MajorAxisLength, 
           -AreaShape_MinorAxisLength, 
           -AreaShape_MaxFeretDiameter,
           -AreaShape_MinFeretDiameter,
           -AreaShape_Eccentricity,
           -AreaShape_Area) %>% # Remove identical metrics from matlab and CellProfiler
    dplyr::select(-OriginalId, -contains("Image_FileName_"),
           -contains("MaxFeretCoordinates"), -contains("MinFeretCoordinates"), 
           -contains("Orientation"), -contains("MaxFeretAngle"), -contains("MinFeretAngle"), 
           -contains("wrampAngle"), -contains("secondAngle"), -contains("majAngle"), 
           -contains("Center_X"), -contains("Center_Y"), -contains("Center_Z"), -contains("Location_"), 
           -contains("BoundingBoxM"), -contains("EulerNumber")) # Remove coordinate-based metrics and nonnumeric info. 
  
  texturize <- function(cpSubscript, chName){
    metricsTexture <- metrics %>% 
      dplyr::select(Object, contains("Texture"), contains("Intensity_StdIntensityEdge"), contains("Intensity_MeanIntensity"), contains("Intensity_StdIntensity")) %>%
      dplyr::select(Object, contains(cpSubscript)) %>%
      rename_with(~gsub(cpSubscript, '', .x), .cols = everything()) %>%
      rowwise() %>%
      dplyr::mutate(Texture_AngularSecondMoment_2_Mean = mean(c(Texture_AngularSecondMoment_2_00_256, Texture_AngularSecondMoment_2_01_256, Texture_AngularSecondMoment_2_02_256, Texture_AngularSecondMoment_2_03_256)),
           Texture_AngularSecondMoment_8_Mean = mean(c(Texture_AngularSecondMoment_8_00_256, Texture_AngularSecondMoment_8_01_256, Texture_AngularSecondMoment_8_02_256, Texture_AngularSecondMoment_8_03_256)),
           Texture_Contrast_2_Mean = mean(c(Texture_Contrast_2_00_256, Texture_Contrast_2_01_256, Texture_Contrast_2_02_256, Texture_Contrast_2_03_256)),
           Texture_Contrast_8_Mean = mean(c(Texture_Contrast_8_00_256, Texture_Contrast_8_01_256, Texture_Contrast_8_02_256, Texture_Contrast_8_03_256)),
           Texture_Correlation_2_Mean = mean(c(Texture_Correlation_2_00_256, Texture_Correlation_2_01_256, Texture_Correlation_2_02_256, Texture_Correlation_2_03_256)),
           Texture_Correlation_8_Mean = mean(c(Texture_Correlation_8_00_256, Texture_Correlation_8_01_256, Texture_Correlation_8_02_256, Texture_Correlation_8_03_256)),
           Texture_DifferenceEntropy_2_Mean = mean(c(Texture_DifferenceEntropy_2_00_256, Texture_DifferenceEntropy_2_01_256, Texture_DifferenceEntropy_2_02_256, Texture_DifferenceEntropy_2_03_256)),
           Texture_DifferenceEntropy_8_Mean = mean(c(Texture_DifferenceEntropy_8_00_256, Texture_DifferenceEntropy_8_01_256, Texture_DifferenceEntropy_8_02_256, Texture_DifferenceEntropy_8_03_256)),
           Texture_DifferenceVariance_2_Mean = mean(c(Texture_DifferenceVariance_2_00_256, Texture_DifferenceVariance_2_01_256, Texture_DifferenceVariance_2_02_256, Texture_DifferenceVariance_2_03_256)),
           Texture_DifferenceVariance_8_Mean = mean(c(Texture_DifferenceVariance_8_00_256, Texture_DifferenceVariance_8_01_256, Texture_DifferenceVariance_8_02_256, Texture_DifferenceVariance_8_03_256)),
           Texture_Entropy_2_Mean = mean(c(Texture_Entropy_2_00_256, Texture_Entropy_2_01_256, Texture_Entropy_2_02_256, Texture_Entropy_2_03_256)),
           Texture_Entropy_8_Mean = mean(c(Texture_Entropy_8_00_256, Texture_Entropy_8_01_256, Texture_Entropy_8_02_256, Texture_Entropy_8_03_256)),
           Texture_InfoMeas1_2_Mean = mean(c(Texture_InfoMeas1_2_00_256, Texture_InfoMeas1_2_01_256, Texture_InfoMeas1_2_02_256, Texture_InfoMeas1_2_03_256)),
           Texture_InfoMeas1_8_Mean = mean(c(Texture_InfoMeas1_8_00_256, Texture_InfoMeas1_8_01_256, Texture_InfoMeas1_8_02_256, Texture_InfoMeas1_8_03_256)),
           Texture_InfoMeas2_2_Mean = mean(c(Texture_InfoMeas2_2_00_256, Texture_InfoMeas2_2_01_256, Texture_InfoMeas2_2_02_256, Texture_InfoMeas2_2_03_256)),
           Texture_InfoMeas2_8_Mean = mean(c(Texture_InfoMeas2_8_00_256, Texture_InfoMeas2_8_01_256, Texture_InfoMeas2_8_02_256, Texture_InfoMeas2_8_03_256)),
           Texture_InverseDifferenceMoment_2_Mean = mean(c(Texture_InverseDifferenceMoment_2_00_256, Texture_InverseDifferenceMoment_2_01_256, Texture_InverseDifferenceMoment_2_02_256, Texture_InverseDifferenceMoment_2_03_256)),
           Texture_InverseDifferenceMoment_8_Mean = mean(c(Texture_InverseDifferenceMoment_8_00_256, Texture_InverseDifferenceMoment_8_01_256, Texture_InverseDifferenceMoment_8_02_256, Texture_InverseDifferenceMoment_8_03_256)),
           Texture_SumAverage_2_Mean = mean(c(Texture_SumAverage_2_00_256, Texture_SumAverage_2_01_256, Texture_SumAverage_2_02_256, Texture_SumAverage_2_03_256)),
           Texture_SumAverage_8_Mean = mean(c(Texture_SumAverage_8_00_256, Texture_SumAverage_8_01_256, Texture_SumAverage_8_02_256, Texture_SumAverage_8_03_256)),
           Texture_SumEntropy_2_Mean = mean(c(Texture_SumEntropy_2_00_256, Texture_SumEntropy_2_01_256, Texture_SumEntropy_2_02_256, Texture_SumEntropy_2_03_256)),
           Texture_SumEntropy_8_Mean = mean(c(Texture_SumEntropy_8_00_256, Texture_SumEntropy_8_01_256, Texture_SumEntropy_8_02_256, Texture_SumEntropy_8_03_256)),
           Texture_SumVariance_2_Mean = mean(c(Texture_SumVariance_2_00_256, Texture_SumVariance_2_01_256, Texture_SumVariance_2_02_256, Texture_SumVariance_2_03_256)),
           Texture_SumVariance_8_Mean = mean(c(Texture_SumVariance_8_00_256, Texture_SumVariance_8_01_256, Texture_SumVariance_8_02_256, Texture_SumVariance_8_03_256)),
           Texture_Variance_2_Mean = mean(c(Texture_Variance_2_00_256, Texture_Variance_2_01_256, Texture_Variance_2_02_256, Texture_Variance_2_03_256)),
           Texture_Variance_8_Mean = mean(c(Texture_Variance_8_00_256, Texture_Variance_8_01_256, Texture_Variance_8_02_256, Texture_Variance_8_03_256)),
           Texture_AngularSecondMoment_2_Range = diff(range(c(Texture_AngularSecondMoment_2_00_256, Texture_AngularSecondMoment_2_01_256, Texture_AngularSecondMoment_2_02_256, Texture_AngularSecondMoment_2_03_256))),
           Texture_AngularSecondMoment_8_Range = diff(range(c(Texture_AngularSecondMoment_8_00_256, Texture_AngularSecondMoment_8_01_256, Texture_AngularSecondMoment_8_02_256, Texture_AngularSecondMoment_8_03_256))),
           Texture_Contrast_2_Range = diff(range(c(Texture_Contrast_2_00_256, Texture_Contrast_2_01_256, Texture_Contrast_2_02_256, Texture_Contrast_2_03_256))),
           Texture_Contrast_8_Range = diff(range(c(Texture_Contrast_8_00_256, Texture_Contrast_8_01_256, Texture_Contrast_8_02_256, Texture_Contrast_8_03_256))),
           Texture_Correlation_2_Range = diff(range(c(Texture_Correlation_2_00_256, Texture_Correlation_2_01_256, Texture_Correlation_2_02_256, Texture_Correlation_2_03_256))),
           Texture_Correlation_8_Range = diff(range(c(Texture_Correlation_8_00_256, Texture_Correlation_8_01_256, Texture_Correlation_8_02_256, Texture_Correlation_8_03_256))),
           Texture_DifferenceEntropy_2_Range = diff(range(c(Texture_DifferenceEntropy_2_00_256, Texture_DifferenceEntropy_2_01_256, Texture_DifferenceEntropy_2_02_256, Texture_DifferenceEntropy_2_03_256))),
           Texture_DifferenceEntropy_8_Range = diff(range(c(Texture_DifferenceEntropy_8_00_256, Texture_DifferenceEntropy_8_01_256, Texture_DifferenceEntropy_8_02_256, Texture_DifferenceEntropy_8_03_256))),
           Texture_DifferenceVariance_2_Range = diff(range(c(Texture_DifferenceVariance_2_00_256, Texture_DifferenceVariance_2_01_256, Texture_DifferenceVariance_2_02_256, Texture_DifferenceVariance_2_03_256))),
           Texture_DifferenceVariance_8_Range = diff(range(c(Texture_DifferenceVariance_8_00_256, Texture_DifferenceVariance_8_01_256, Texture_DifferenceVariance_8_02_256, Texture_DifferenceVariance_8_03_256))),
           Texture_Entropy_2_Range = diff(range(c(Texture_Entropy_2_00_256, Texture_Entropy_2_01_256, Texture_Entropy_2_02_256, Texture_Entropy_2_03_256))),
           Texture_Entropy_8_Range = diff(range(c(Texture_Entropy_8_00_256, Texture_Entropy_8_01_256, Texture_Entropy_8_02_256, Texture_Entropy_8_03_256))),
           Texture_InfoMeas1_2_Range = diff(range(c(Texture_InfoMeas1_2_00_256, Texture_InfoMeas1_2_01_256, Texture_InfoMeas1_2_02_256, Texture_InfoMeas1_2_03_256))),
           Texture_InfoMeas1_8_Range = diff(range(c(Texture_InfoMeas1_8_00_256, Texture_InfoMeas1_8_01_256, Texture_InfoMeas1_8_02_256, Texture_InfoMeas1_8_03_256))),
           Texture_InfoMeas2_2_Range = diff(range(c(Texture_InfoMeas2_2_00_256, Texture_InfoMeas2_2_01_256, Texture_InfoMeas2_2_02_256, Texture_InfoMeas2_2_03_256))),
           Texture_InfoMeas2_8_Range = diff(range(c(Texture_InfoMeas2_8_00_256, Texture_InfoMeas2_8_01_256, Texture_InfoMeas2_8_02_256, Texture_InfoMeas2_8_03_256))),
           Texture_InverseDifferenceMoment_2_Range = diff(range(c(Texture_InverseDifferenceMoment_2_00_256, Texture_InverseDifferenceMoment_2_01_256, Texture_InverseDifferenceMoment_2_02_256, Texture_InverseDifferenceMoment_2_03_256))),
           Texture_InverseDifferenceMoment_8_Range = diff(range(c(Texture_InverseDifferenceMoment_8_00_256, Texture_InverseDifferenceMoment_8_01_256, Texture_InverseDifferenceMoment_8_02_256, Texture_InverseDifferenceMoment_8_03_256))),
           Texture_SumAverage_2_Range = diff(range(c(Texture_SumAverage_2_00_256, Texture_SumAverage_2_01_256, Texture_SumAverage_2_02_256, Texture_SumAverage_2_03_256))),
           Texture_SumAverage_8_Range = diff(range(c(Texture_SumAverage_8_00_256, Texture_SumAverage_8_01_256, Texture_SumAverage_8_02_256, Texture_SumAverage_8_03_256))),
           Texture_SumEntropy_2_Range = diff(range(c(Texture_SumEntropy_2_00_256, Texture_SumEntropy_2_01_256, Texture_SumEntropy_2_02_256, Texture_SumEntropy_2_03_256))),
           Texture_SumEntropy_8_Range = diff(range(c(Texture_SumEntropy_8_00_256, Texture_SumEntropy_8_01_256, Texture_SumEntropy_8_02_256, Texture_SumEntropy_8_03_256))),
           Texture_SumVariance_2_Range = diff(range(c(Texture_SumVariance_2_00_256, Texture_SumVariance_2_01_256, Texture_SumVariance_2_02_256, Texture_SumVariance_2_03_256))),
           Texture_SumVariance_8_Range = diff(range(c(Texture_SumVariance_8_00_256, Texture_SumVariance_8_01_256, Texture_SumVariance_8_02_256, Texture_SumVariance_8_03_256))),
           Texture_Variance_2_Range = diff(range(c(Texture_Variance_2_00_256, Texture_Variance_2_01_256, Texture_Variance_2_02_256, Texture_Variance_2_03_256))),
           Texture_Variance_8_Range = diff(range(c(Texture_Variance_8_00_256, Texture_Variance_8_01_256, Texture_Variance_8_02_256, Texture_Variance_8_03_256)))) 
    metricsTexture <- metricsTexture %>%
      ungroup() %>%
      dplyr::mutate(CV_IntensityEdge = Intensity_StdIntensityEdge/Intensity_MeanIntensityEdge,
           CV_IntensityCell = Intensity_StdIntensity/Intensity_MeanIntensity) %>%
      dplyr::select(-Intensity_MeanIntensity, -Intensity_StdIntensity, -Intensity_StdIntensityEdge, -Intensity_MeanIntensityEdge) %>%
      rename_with(~str_c(., paste("_", chName, sep = "")), .cols = everything()) %>%
      dplyr::select(-contains("_256"))
  }
  metricsTexture1 <- texturize(cpSubscript1, chName1)
  metricsTexture2 <- texturize(cpSubscript2, chName2)
  if(chName3 != "empty"){metricsTexture3 <- texturize(cpSubscript3, chName3)}
  
  metrics2 <- merge(metrics %>% dplyr::select(-contains("Texture")), metricsTexture1, by.x = "Object", by.y = paste("Object_", chName1, sep = ""))
  metrics3 <- merge(metrics2, metricsTexture2, by.x = "Object", by.y = paste("Object_", chName2, sep = ""))
  if(chName3 != "empty"){
    metrics4 <- merge(metrics3, metricsTexture3, by.x = "Object", by.y = paste("Object_", chName3, sep = ""))
    metricsAll <- metrics4
  }else{
    metricsAll <- metrics3
  }
  
  metricsAll <- metricsAll %>%
      dplyr::select(-contains("Intensity_MeanIntensity_"))
  
  tooSmall <- c(metricsAll %>% filter(Area < 17000 | MaxFeretDiameter < 350) %>% dplyr::select(Object), metrics2 %>% filter(MaxFeretDiameter < 400, Area < 34000) %>% dplyr::select(Object))
  metricsClean <- metricsAll %>%
   filter(!Object %in% tooSmall[[1]], !Object %in% tooSmall[[2]])
}

# Function to rename normAreaFeatures to be specific to a certain channel's variable names:
normAreaFeaturesChannel <- function(normAreaFeatures, chName){
  chInvariantFeatures <- c("Area", "MajorAxisLength", "MinorAxisLength",  "Eccentricity", "MaxFeretDiameter", "MinFeretDiameter", "AreaShape_BoundingBoxArea", "AreaShape_ConvexArea", "AreaShape_EquivalentDiameter", "AreaShape_MaximumRadius", "AreaShape_MeanRadius", "AreaShape_MedianRadius", "AreaShape_Perimeter")

  normAreaChFeatures <- setdiff(normAreaFeatures, chInvariantFeatures) %>%
    str_c(., paste("_", chName, sep = ""))
  features <- c(chInvariantFeatures, normAreaChFeatures)
}

# Function to calculate the median of each area feature across the control condition of cells in the training experiment
controlMedianAreas <- function(metricsClean, normAreaFeatures, manual){
  medianAreas <- metricsClean %>%
    filter(Object %in% manual$Object) %>% # Remove incorrectly segmented (not a single cell) objects
    dplyr::select(all_of(normAreaFeatures), "Normalization") %>%
    filter(Normalization == "Control") %>%
    group_by(Normalization) %>%
    summarize_all(median, na.rm = T) %>%
    ungroup() %>%
    dplyr::select(-Normalization)
} 

# This function scales area-based features by dividing by the median value of cells in the training experiment (control-condition only). It also normalizes intensity values (to account for variability between conditions and experiments collected on different days) by providing values in relative terms (dividing measurements by the mean or integrated intensity of the cell). It is intended for use on V1 features. Features that are already expressed as a proportion or a [0 1] scale are not changed (e.g., profile measurement, relative area, wrampHalves, brightPix, etc.).
scaleAreaIntensity <- function(metrics, normAreaFeatures, controlMedian, colocFeatures, chName, cpSubscript){
  areaMetrics <- dplyr::select(metrics, all_of(normAreaFeatures))
  scaleArea <- as.data.frame(mapply('/', areaMetrics, controlMedian)) #%>%
    #dplyr::mutate_all(log)
  
  annotFeatures <- c("Object", "Image", "Experiment", "Replicate", "Coverslip", "Condition", "mainCondition", "mainReplicate", "experimentGroup", "Normalization")
  normNonArea <- metrics %>%
    dplyr::select(-all_of(colocFeatures)) %>%
    dplyr::select(-all_of(normAreaFeatures)) %>%
    dplyr::select(any_of(annotFeatures), contains(paste("_", chName, sep = "")), contains(cpSubscript)) %>%
    rename_with(~gsub(cpSubscript, '', .x), .cols = contains(cpSubscript)) %>%
    rename_with(~gsub(paste("_", chName, sep = ""), '', .x), .cols = contains(paste("_", chName, sep = ""))) %>%
    dplyr::select(-largeObj, -brightMeanObj, -brightSumObj) %>%
    dplyr::mutate(angleWramp2Major = angleWramp2Major/90,
           angleSecond2Major = angleSecond2Major/90,
           angleWramp2Second = angleWramp2Second/180,
           intensityWrampHalves = log(intensityWrampHalves),
           intensityMajorHalves = log(intensityMajorHalves),
           intensitySecondHalves = log(intensitySecondHalves),
           medianObjectMeanIntensity = medianObjectMeanIntensity/meanIntensityCell, # Fixed
           medianObjectSumIntensity = medianObjectSumIntensity/sumIntensityCell,   # Fixed
           meanIntensityWramp = meanIntensityWramp/meanIntensityCell,
           medianIntensityWramp = medianIntensityWramp/medianIntensityCell,
           meanIntensityBrightObj = meanIntensityBrightObj/meanIntensityCell,
           sumIntensityBrightObj = sumIntensityBrightObj/sumIntensityCell,
           sumIntensityWramp = sumIntensityWramp/sumIntensityCell,
           sumIntensityNotWramp = sumIntensityNotWramp/sumIntensityCell, 
           sumIntensityNotBright = sumIntensityNotBright/sumIntensityCell, 
           sumIntensitySecond = sumIntensitySecond/sumIntensityCell,
           meanIntensityNotWramp = meanIntensityNotWramp/meanIntensityCell,
           medianIntensityNotWramp = medianIntensityNotWramp/medianIntensityCell,
           meanIntensityNotBright = meanIntensityNotBright/meanIntensityCell,
           medianIntensityNotBright = medianIntensityNotBright/medianIntensityCell,
           meanIntensitySecond = meanIntensitySecond/meanIntensityCell,
           medianIntensitySecond = medianIntensitySecond/medianIntensityCell) %>%
    dplyr::mutate(Intensity_LowerQuartileIntensity = Intensity_LowerQuartileIntensity/meanIntensityCell, 
                  Intensity_MADIntensity = Intensity_MADIntensity/meanIntensityCell,
                  Intensity_MaxIntensityEdge = Intensity_MaxIntensityEdge/meanIntensityCell,
                  Intensity_MaxIntensity = Intensity_MaxIntensity/meanIntensityCell,
                  Intensity_MeanIntensityEdge = Intensity_MeanIntensityEdge/meanIntensityCell,
                  Intensity_MinIntensityEdge = Intensity_MinIntensityEdge/meanIntensityCell,
                  Intensity_MinIntensity = Intensity_MinIntensity/meanIntensityCell,
                  Intensity_UpperQuartileIntensity = Intensity_UpperQuartileIntensity/meanIntensityCell) %>%
    dplyr::select(-meanIntensityCell, -medianIntensityCell, -sumIntensityCell, -Intensity_StdIntensityEdge, -Intensity_StdIntensity, 
           -contains("MeanFrac_")) %>%
    rename_with(~str_c(., paste("_", chName, sep = "")), .cols = -contains(annotFeatures))
  
  normMetrics <- cbind(normNonArea, scaleArea)
}

# Confusion matrix of ML classification (prediction) vs. manual scoring (reference)
# Supply fit from caret to function
analyzeResults <- function(dataset, fit, score, conditionName){
  dataset <- dplyr::select(dataset, -Normalization) %>%
    rename(refScore = score,
           useCondition = conditionName)
  Prediction <- predict(fit, dataset)
  Reference <- dataset$refScore
  ConditionGroup <- dataset$useCondition
  Confidence <- dplyr::select(dataset, contains("Confidence"))
  confusData <- data.frame(as.character(Prediction), as.character(Reference), ConditionGroup, Confidence) %>%
    dplyr::mutate(Prediction = factor(Prediction, levels = c("OneEnd", "BothEnds", "None")),
           Reference = factor(Reference, levels = c("OneEnd", "BothEnds", "None")))

  conditions <- unique(confusData$ConditionGroup)
  for(val in 1:length(conditions)){
    print(conditions[val])
    print(caret::confusionMatrix(confusData$Prediction[confusData$ConditionGroup == conditions[val]],
                      confusData$Reference[confusData$ConditionGroup == conditions[val]]))
    print("High Confidence")
    print(caret::confusionMatrix(confusData$Prediction[confusData$ConditionGroup == conditions[val] & confusData$Confidence !=2],
                      confusData$Reference[confusData$ConditionGroup == conditions[val] & confusData$Confidence != 2]))
  }
  
  ggplot(confusData, aes(x = ConditionGroup)) + geom_bar(aes(fill = Prediction), position = position_fill(reverse = T))
}

# Alternate function for generating confusion matrix. Add ML classification as a variable to the dataset before inputting to function. Provide names of both variables to compare (e.g., ML classification and manual score)
analyzeResults2 <- function(dataset, className, score, conditionName){
  dataset <- dplyr::select(dataset, -Normalization) %>%
    dplyr::rename(Prediction = className,
                  refScore = score,
                  useCondition = conditionName)
  Prediction <- dataset$Prediction
  Reference <- dataset$refScore
  ConditionGroup <- dataset$useCondition
  Confidence <- dplyr::select(dataset, contains("Confidence"))
  
  confusData <- data.frame(as.character(Prediction), as.character(Reference), ConditionGroup, Confidence) %>%
    dplyr::mutate(Prediction = factor(Prediction, levels = c("OneEnd", "BothEnds", "None")),
           Reference = factor(Reference, levels = c("OneEnd", "BothEnds", "None")))
  
  conditions <- unique(confusData$ConditionGroup)
  for(val in 1:length(conditions)){
    print(conditions[val])
    print(caret::confusionMatrix(confusData$Prediction[confusData$ConditionGroup == conditions[val]],
                      confusData$Reference[confusData$ConditionGroup == conditions[val]]))
    print("High Confidence")
    print(caret::confusionMatrix(confusData$Prediction[confusData$ConditionGroup == conditions[val] & confusData$Confidence !=2],
                      confusData$Reference[confusData$ConditionGroup == conditions[val] & confusData$Confidence != 2]))
  }
  
  ggplot(confusData, aes(x = ConditionGroup)) + geom_bar(aes(fill = Prediction), position = position_fill(reverse = T))
}

# Wrapper function to fit two models and generate a combined classification where both classifiers must agree on one-ended WRAMP structures (reduces false positives at the cost of sensitivity). Classes are added to the metricsClean dataframe.
classifyCleanMetricsCombinedModels <- function(metricsCleaned, metricsScaled, fit1, fit2, columnName){
  metricsCleaned <- arrange(metricsCleaned, Object)
  metricsScaled <- arrange(metricsScaled, Object)
  metricsCleaned$prediction1 <- predict(fit1, metricsScaled)
  metricsCleaned$prediction2 <- predict(fit2, metricsScaled)
  metricsCleaned <- metricsCleaned %>%
    dplyr::mutate(prediction1 = as.character(prediction1), prediction2 = as.character(prediction2)) %>%
    dplyr::mutate(combo = ifelse((prediction1 == "OneEnd" & prediction2 != "OneEnd"), "None", prediction1)) %>%
    dplyr::mutate_at(c("prediction1", "prediction2", "combo"), function(x){factor(x, levels = c("OneEnd", "BothEnds", "None"))}) %>%
    dplyr::select(-prediction1, -prediction2) %>%
    dplyr::rename_with(~ gsub("combo", columnName, .x), .cols = "combo")
}

# Wrapper function to fit two models and generate a combined classification where both classifiers must agree on one-ended WRAMP structures (reduces false positives at the cost of sensitivity). Classes are added to the metricsClean dataframe.
classifyCleanMetricsCombinedModels <- function(metricsCleaned, metricsScaled, fit1, fit2, columnName){
  metricsCleaned <- arrange(metricsCleaned, Object)
  metricsScaled <- arrange(metricsScaled, Object)
  metricsCleaned$prediction1 <- predict(fit1, metricsScaled)
  metricsCleaned$prediction2 <- predict(fit2, metricsScaled)
  metricsCleaned <- metricsCleaned %>%
    dplyr::mutate(prediction1 = as.character(prediction1), prediction2 = as.character(prediction2)) %>%
    dplyr::mutate(combo = ifelse((prediction1 == "OneEnd" & prediction2 != "OneEnd"), "None", prediction1)) %>%
    dplyr::mutate_at(c("prediction1", "prediction2", "combo"), function(x){factor(x, levels = c("OneEnd", "BothEnds", "None"))}) %>%
    dplyr::select(-prediction1, -prediction2) %>%
    dplyr::rename_with(~ gsub("combo", columnName, .x), .cols = "combo")
}

# Wrapper to apply a single classifer to the data
classifyCleanMetricsOneModel <- function(metricsCleaned, metricsScaled, fit1, fit2, columnName){
  metricsCleaned <- arrange(metricsCleaned, Object)
  metricsScaled <- arrange(metricsScaled, Object)
  metricsCleaned$prediction1 <- predict(fit1, metricsScaled)
  metricsCleaned <- metricsCleaned %>%
  dplyr::rename_with(~ gsub("prediction1", columnName, .x), .cols = "prediction1")
}
```

Annotation files
```{r}
experimentGroup <- data.frame(experimentGroup = c("20210210KD", "20210406KD", "20210513KD", "202107KD", "202107KD", "202107KD", "202107KD", "20211205KD", "20211205KD", "20211205KD", "20211205KD", "20220509KD", "20220530KD"),
                              Experiment = c("20210210_EzrinKD", "20210406_KD", "20210513_MoesinKD", "20210723_KD1", "20210726_KD1", "20210728_KD2", "20210805_KD3", "20211205_KD_EZR_RepN", "20211205_KD_MSN_RepN", "20211205_KD_RDX_StainMyoIIB_RepN", "20211205_KD_RhoA_RepN", "20220509KD", "20220530_KD_RDX"))

annotation0513 <- read.csv(paste(dirPath, "20210513Transfection/Annotation20210513KD.csv", sep = "")) %>%
  dplyr::mutate(mainCondition = str_remove(Condition, "_Stain.*")) %>%
  dplyr::mutate(mainCondition = str_remove(mainCondition, ".*_")) %>%
  dplyr::mutate(mainRep = str_remove(Replicate, "_Stain.*")) %>%
  merge(experimentGroup, by = "Experiment")

annotationOld <- read.csv(paste(dirPath, "OlderExperiments/OlderKnockdowns_Annotation.csv", sep = "")) %>%
  dplyr::mutate(mainCondition = str_remove(Condition, "_Stain.*")) %>%
  dplyr::mutate(mainCondition = str_remove(mainCondition, ".*_")) %>%
  dplyr::mutate(mainRep = str_remove(Replicate, "_Stain.*")) %>%
  merge(experimentGroup, by = "Experiment")

annotation1205 <- read.csv(paste(dirPath, "20211205Transfection/20211205KD_Annotation.csv", sep = "")) %>%
  dplyr::mutate(mainCondition = str_remove(Condition, "_Stain.*")) %>%
  dplyr::mutate(mainCondition = str_remove(mainCondition, ".*_")) %>%
  dplyr::mutate(mainRep = str_remove(Replicate, "_Stain.*")) %>%
  merge(experimentGroup, by = "Experiment") %>%
  dplyr::mutate(Condition = str_remove(Condition, "20220509_")) %>% # Fix problem with annotation file
  dplyr::mutate(Condition = str_remove(Condition, "_KD.*"))

annotation0509 <- read.csv(paste(dirPath, "20220509Transfection/20220509KD_Annotation.csv", sep = "")) %>%
  dplyr::mutate(mainCondition = str_remove(Condition, "_Stain.*")) %>%
  dplyr::mutate(mainCondition = str_remove(mainCondition, ".*_")) %>%
  dplyr::mutate(mainRep = str_remove(Replicate, "_Stain.*")) %>%
  merge(experimentGroup, by = "Experiment") %>%
  dplyr::mutate(Condition = str_remove(Condition, "20220509_")) %>% # Fix problem with annotation file
  dplyr::mutate(Condition = str_remove(Condition, "_KD.*"))

annotation0530 <- read_csv(paste(dirPath, "20220530Transfection/Annotation_20220530KD.csv", sep = "")) %>%
  dplyr::mutate(mainCondition = str_remove(Condition, "_Stain.*")) %>%
  dplyr::mutate(mainCondition = str_remove(mainCondition, ".*_")) %>%
  dplyr::mutate(mainRep = str_remove(Replicate, "_Stain.*")) %>%
  merge(experimentGroup, by = "Experiment")

annotation <- rbind(annotation0513 %>% select(all_of(colnames(annotation1205))),
                    annotationOld %>% select(all_of(colnames(annotation1205))),
                    annotation1205, 
                    annotation0509 %>% select(all_of(colnames(annotation1205))),
                    annotation0530 %>% select(all_of(colnames(annotation1205))))

  

excludeImages <- c("KD_EZR_MCAM_Myosin_Cov2_001.nd2", "KD_RhoA_Actin_Myosin_cov1_002.nd2", "KD_RDX_Myosin_cov1_003.nd2", "Cntr_EZR_MCAM_Actin_Cov2_007.nd2", "Cntr_RhoA_Actin_ROCK1_2_cov1_006")

#write.csv(annotation, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/allAnnotation20221101.csv", sep = ""), row.names = F)

## Check combined annotation file for errors
unique(select(annotation, experimentGroup, Experiment, mainRep))
unique(select(annotation, mainRep, Condition, Replicate))
unique(annotation$Condition)
```

Cell Profiler files:
```{r}
# Two-channel images
cp0513 <- readCp(paste(dirPath, "20210513Transfection/CellProfiler/Output/20220404_CellProfiler_NoNegVals_Image.csv", sep = ""), paste(dirPath, "20210513Transfection/CellProfiler/Output/20220404_CellProfiler_NoNegVals_Cell.csv", sep = ""))

cpOldPt1 <- readCp(paste(dirPath, "OlderExperiments/CellProfiler/Output/20220507_CellProfiler_NoNegVal_MCAM_Pt1Image.csv", sep = ""), paste(dirPath, "OlderExperiments/CellProfiler/Output/20220507_CellProfiler_NoNegVal_MCAM_Pt1Cell.csv", sep = ""))

# Three-channel images
cpOldPt2 <- readCp(paste(dirPath, "OlderExperiments/CellProfiler/Output/20220507_CellProfiler_NoNegVal_MCAM_Pt2Image.csv", sep = ""), paste(dirPath, "OlderExperiments/CellProfiler/Output/20220507_CellProfiler_NoNegVal_MCAM_Pt2Cell.csv", sep = ""))

cp1205 <- readCp(paste(dirPath, "20211205Transfection/CellProfiler/Output/20220210_CellProfiler_NoNegVals_Image.csv", sep = ""), paste(dirPath, "20211205Transfection/CellProfiler/Output/20220210_CellProfiler_NoNegVals_Cell.csv", sep = "")) %>%
  rename_with(~gsub("Mcam", 'Main', .x), .cols = everything())  %>%
  rename_with(~gsub("Factin", 'Third', .x), .cols = everything())

cp0509 <- readCp(paste(dirPath, "20220509Transfection/CellProfiler/Output/20220523_CellProfiler_NoNegVal_20220509TfnImage.csv", sep = ""), paste(dirPath, "20220509Transfection/CellProfiler/Output/20220523_CellProfiler_NoNegVal_20220509TfnCell.csv", sep = ""))

cp0530 <- readCp(paste(dirPath, "20220530Transfection/CellProfiler/Output/20220612_CellProfiler_NoNegVal_20220530TfnImage.csv", sep = ""), paste(dirPath, "20220530Transfection/CellProfiler/Output/20220612_CellProfiler_NoNegVal_20220530TfnCell.csv", sep = ""))

# Check column names match after renaming according to updated format (setdiff should be empty)
setdiff(colnames(cp1205), colnames(cpOldPt2))

cp2channel <- rbind(cp0513, cpOldPt1)
cp3channel <- rbind(cpOldPt2, cp1205, cp0509, cp0530)
```

Matlab files:
```{r}
matlab0513 <- importMatlabMulti(paste(dirPath, "20210513Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Cell_20220404.csv", sep = ""), paste(dirPath, "20210513Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_MCAM_20220404.csv", sep = ""), paste(dirPath, "20210513Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Other_20220404.csv", sep = ""), "empty", annotation0513, "MCAM", "Other", "empty")

matlabOld <- importMatlabMulti(paste(dirPath, "OlderExperiments/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Cell_20220506.csv", sep = ""), paste(dirPath, "OlderExperiments/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_MCAM_20220506.csv", sep = ""), paste(dirPath, "OlderExperiments/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Other_20220506.csv", sep = ""), paste(dirPath, "OlderExperiments/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Factin_20220506.csv", sep=""), annotationOld, "MCAM", "Other", "Third")
# Image 22_Cov1_001 was duplicated in Matlab analysis, but duplicate rows are removed during import

matlab1205 <- importMatlabMulti(paste(dirPath, "20211205Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Cell_20220410.csv", sep = ""), paste(dirPath, "20211205Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_MCAM_20220410.csv", sep = ""), paste(dirPath, "20211205Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Other_20220410.csv", sep = ""),
                                paste(dirPath, "20211205Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Factin_20220410.csv", sep = ""), annotation1205, "MCAM", "Other", "Third") 
#Note some images not in annotation file, but conveniently from RDX knockdown

matlab0509Pt1 <- importMatlabMulti(paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Cell_20220521.csv", sep = ""), paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_MCAM_20220521.csv", sep = ""), paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Other_20220521.csv", sep = ""),
                                paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Factin_20220521.csv", sep = ""), annotation0509, "MCAM", "Other", "Third")

matlab0509Pt2 <- importMatlabMulti(paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Cell_20220522.csv", sep = ""), paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_MCAM_20220522.csv", sep = ""), paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Other_20220522.csv", sep = ""),
                                paste(dirPath, "20220509Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Factin_20220522.csv", sep = ""), annotation0509, "MCAM", "Other", "Third")

matlab0509 <- rbind(matlab0509Pt1, matlab0509Pt2)
remove(matlab0509Pt1)
remove(matlab0509Pt2)

matlab0530 <- importMatlabMulti(paste(dirPath, "20220530Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Cell_20220611.csv", sep = ""), paste(dirPath, "20220530Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_MCAM_20220611.csv", sep=""), paste(dirPath, "20220530Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Other_20220611.csv", sep = ""),
                                paste(dirPath, "20220530Transfection/MatlabAnalysis/WrampMetrics/Output/80thPctlNoCloseStats_Factin_20220611.csv", sep = ""), annotation0530, "MCAM", "Other", "Third")

matlab2channel <- rbind(matlab0513 %>%
  dplyr::select(-TxRed), 
                        matlabOld %>% 
                          filter(Object %in% cpOldPt1$Object) %>% 
                          dplyr::select(all_of(colnames(matlab0513 %>% dplyr::select(-TxRed))))) %>%
  dplyr::select(-all_of(c("DAPI", "FITC")))

matlab3channel <- rbind(matlabOld %>% 
                          filter(Object %in% cpOldPt2$Object) %>% 
                          dplyr::select(-all_of(c("DAPI", "FITC", "TxRedCy5"))), 
                        matlab1205,
                        matlab0509 %>%
                          dplyr::select(-all_of(c("DAPI", "FITC", "TxRedCy5"))),
                        matlab0530 %>%
                          dplyr::select(-all_of(c("DAPI", "FITC", "TxRedCy5"))))

# Check that object names match in Matlab and CellProfiler dataframes (setdiff should be empty)
setdiff(matlab2channel$Object, cp2channel$Object)
setdiff(matlab3channel$Object, cp3channel$Object) # Note: cp files are usually several rows longer because Matlab skips segmented objects that fail the function (usually very weirdly shaped mask from debris or rounded cell that the function can't accomodate)
```

Combine and clean features
```{r}
metricsClean2Channel <- combineMetrics(matlab2channel, cp2channel, "_BgSubtractedMain", "_BgSubtractedOther", "empty", "MCAM", "Other", "empty")

metricsClean3Channel  <- combineMetrics(matlab3channel, cp3channel, "_BgSubtractedMain", "_BgSubtractedOther", "_BgSubtractedThird", "MCAM", "Other", "Third")

# write_csv(metricsClean2Channel, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/metricsClean_2Channel_Thesis_20221104test.csv", sep = ""))
# write_csv(metricsClean3Channel, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/metricsClean_3Channel_Thesis_20221104test.csv", sep = ""))
```

Compile 2- and 3-channel datasets (removing 3rd channel - phalloidin)
```{r}
metricsCleanMcamOtherAllMcam488 <- rbind(metricsClean2Channel,
                               metricsClean3Channel %>% dplyr::select(-all_of(setdiff(colnames(metricsClean3Channel), colnames(metricsClean2Channel))))) %>%
    filter(Exclude != "Omit" | is.na(Exclude), 
           !str_detect(Replicate, "StainCD44"), 
           !str_detect(Replicate, "StainMCAMC"),
           !str_detect(Image, "RDX488")) %>% # Stained using rabbit MCAM antibody or no MCAM
    filter(str_detect(Condition, "StainMCAM-")) # Redundancy

# write_csv(metricsCleanMcamOtherAllMcam488, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/metricsClean_McamOtherAllMcam488_Thesis_20221104test.csv", sep = ""))
```

Scale and normalize features:
```{r}
normAreaFeaturesGeneric <- read.csv(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/InputForML/ScalingValues/normAreaFeatures.csv", sep = ""))[,"x"]

normAreaFeatures.MCAM <- normAreaFeaturesChannel(normAreaFeaturesGeneric, "MCAM")

medianAreas.MCAM <- read.csv(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/InputForML/ScalingValues/medianAreasMcam.csv", sep = ""))

colocFeatures <- read.csv(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/InputForML/ScalingValues/colocalizationFeatures.csv", sep = ""))[,"x"]

metricsScaled.MCAM <- scaleAreaIntensity(metricsCleanMcamOtherAllMcam488, 
                                         normAreaFeatures.MCAM, medianAreas.MCAM, colocFeatures, "MCAM", "_BgSubtractedMain")
metricsScaled.MCAM %>% filter_if(is.numeric, any_vars(is.nan(.)))
metricsCleanMcamOtherAllMcam488 %>% filter(Object == "23_Cov1_001.nd2_17") # Median intensity was 0 so Inf and NaN introduced. This is from February experiment which was not included in paper.

write.csv(metricsScaled.MCAM, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/metricsScaled_McamOtherAllMcam488_Thesis_20221104test_CorrectedCondition.csv", sep = ""))
```

Remove data for extraneous knockdown conditions, different IF staining, excluded experiments, etc.
```{r}
xlabel <- data.frame(mainCondition = c("siCntr", "siEZR", "siRDX", "siMSN"), 
                     xlabel = factor(c("Control", "EZR", "RDX", "MSN"), levels = c("Control", "MSN", "EZR", "RDX")))

metricsCleanMcamOtherMcam488.Filt <- metricsCleanMcamOtherAllMcam488 %>%
  filter(!Image %in% excludeImages) %>% filter(Exclude != "Omit" | is.na(Exclude)) %>% 
  filter(!str_detect(Replicate, "StainCD44"), 
           !str_detect(Replicate, "StainMCAMC"),
           !str_detect(Image, "RDX488")) %>% # Stained using rabbit MCAM antibody or no MCAM
  filter(str_detect(Condition, "StainMCAM-")) %>%
  filter(!experimentGroup %in% c("20210513KD")) %>%
  filter(!Experiment %in% c("20210723_KD1", "20210726_KD1", "20210805_KD3")) %>% # Not included in paper (met exclusion criteria described in Statistics in Supplemental Material)
  filter(Experiment != "20210210_EzrinKD") %>% # Not a replicate condition
  filter(mainRep != "20211205_siRhoA") %>%  # This removes siRhoA images (not control siRNA images with MCAM-ROCK1/2 staining)
  filter(!str_detect(Experiment, "20211205_KD_RDX")) %>% # Control and KD conditions may have been mixed up 
  merge(xlabel, by = "mainCondition") %>%
  dplyr::mutate(Condition = str_remove(Condition, "_KD.*")) %>%
  arrange(Experiment)

unique(metricsCleanMcamOtherMcam488.Filt$Condition)
unique(metricsCleanMcamOtherMcam488.Filt$experimentGroup)

metricsScaled.MCAM.Filt <- metricsScaled.MCAM %>% filter(Object %in% metricsCleanMcamOtherMcam488.Filt$Object)

metricsCleanMcamOtherMcam488.Filt %>%
  group_by(experimentGroup, xlabel, mainCondition, mainRep) %>% count(Replicate)
```

Use ML model trained in separate notebook to classify the data:
```{r}
mcamKDmodel2_85 <- readRDS(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/ClassifiersForMcam/modelList20221104-NoTexture_85up", sep = ""))

metricsCleanMcamOtherMcam488.Classified.Filt <- classifyCleanMetricsCombinedModels(metricsCleanMcamOtherMcam488.Filt, 
                                                                       metricsScaled.MCAM.Filt, 
                                                                       mcamKDmodel2_85[["fittedModels"]][["gbmTwo"]],
                                                                       mcamKDmodel2_85[["fittedModels"]][["extraTreesTwo"]], 
                                                                       columnName = "comboGbmExtraTwo_MCAM2") %>%
  dplyr::mutate(Experiment = ifelse(Experiment == "20210723_KD1", "20210726_KD1", Experiment))

# write_csv(metricsCleanMcamOtherMcam488.Classified.Filt, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/metricsCleanClassified_UsedInPlots_Test.csv", sep=""))
```

Manual scoring used in ML:
```{r}
manualScoringTemp <- read.csv(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/InputForML/manualScoringNoCopolar_20221104_New.csv", sep = "")) %>%
  filter(is.na(Segmentation))
manualScoring <- manualScoringTemp %>%
  filter(is.na(Segmentation)) %>%
  filter(!Image %in% excludeImages) %>% filter(Exclude != "Omit" | is.na(Exclude)) %>% 
  filter(!str_detect(Replicate, "StainCD44"), 
           !str_detect(Replicate, "StainMCAMC"),
           !str_detect(Image, "RDX488")) %>% # Stained using rabbit MCAM antibody or no MCAM
  filter(str_detect(Condition, "StainMCAM-")) %>% # Redundant
  filter(!experimentGroup %in% c("20210513KD")) %>% 
  filter(!Experiment %in% c("20210723_KD1", "20210726_KD1", "20210805_KD3")) %>% # Not included in paper (met exclusion criteria described in Statistics in Supplemental Material)
  filter(Experiment != "20210210_EzrinKD") %>%
  filter(mainRep != "20211205_siRhoA") %>%  # This removes siRhoA images (not control siRNA images with MCAM-ROCK1/2 staining)
  filter(!str_detect(Experiment, "20211205_KD_RDX")) %>% # Control and KD conditions may have been mixed up 
  merge(xlabel, by = "mainCondition") %>%
  dplyr::mutate(Condition = str_remove(Condition, "20220509_")) %>% # Fix problem with annotation file
  dplyr::mutate(Condition = str_remove(Condition, "_KD.*")) %>%
  arrange(Experiment)

# Check that filtering works correctly
setdiff(manualScoring$Object, metricsCleanMcamOtherMcam488.Classified.Filt$Object)
test <- metricsCleanMcamOtherMcam488.Classified.Filt %>% filter(Object %in% manualScoringTemp$Object)
setdiff(test$Object, manualScoring$Object)
remove(test)

# For what % of cells with "OneEnd" MCAM is the brightest object at the polarized region (Wrong Object == "Yes")? 97.5% overall
manualScoring %>%
  filter(is.na(Segmentation)) %>%
  filter(ManualScoreMcam == "OneEnd") %>%
  count(WrongObject) %>%
  dplyr::mutate(perc = n/sum(n)*100, nTot = sum(n)) %>%
  dplyr::mutate(CorrectObject = 100-perc) %>%
  ungroup()

# % of WrongObject cells is higher for siMSN and siRDX
manualScoring %>%
  filter(is.na(Segmentation)) %>%
  filter(ManualScoreMcam == "OneEnd") %>%
  group_by(mainCondition) %>%
  count(WrongObject) %>%
  dplyr::mutate(perc = n/sum(n)*100, nTot = sum(n)) %>%
  ungroup()

# What % of cells is bothEnds? 3% overall
manualScoring %>%
  filter(is.na(Segmentation)) %>%
  count(ManualScoreMcam) %>%
  dplyr::mutate(perc = n/sum(n)*100, nTot = sum(n)) %>%
  ungroup()

# 2-4% of cells per siRNA condition
manualScoring %>%
  filter(is.na(Segmentation)) %>%
  group_by(mainCondition) %>%
  count(ManualScoreMcam) %>%
  dplyr::mutate(perc = n/sum(n)*100, nTot = sum(n)) %>%
  ungroup()
```

Sensitivity and specificity for each round of iterative training for gbm and extraTrees classifiers (Supp. Figure S7A):
```{r}
# Check accuracy for upSampling rounds
analyzeResults(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Zero"]]) %>%
                  dplyr::mutate(All = "All"),
               mcamKDmodel2_85[["fittedModels"]][["gbmZero"]],
               "ManualScoreMcam",
               "All")

nrow(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Zero"]]))
                 
analyzeResults(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["One"]]) %>%
                  dplyr::mutate(All = "All"),
               mcamKDmodel2_85[["fittedModels"]][["gbmOne"]],
               "ManualScoreMcam",
               "All")

nrow(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["One"]]))

analyzeResults(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]) %>%
                  dplyr::mutate(All = "All"),
               mcamKDmodel2_85[["fittedModels"]][["gbmTwo"]],
               "ManualScoreMcam",
               "All")

nrow(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]))

analyzeResults(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Zero"]]) %>%
                  dplyr::mutate(All = "All"),
               mcamKDmodel2_85[["fittedModels"]][["extraTreesZero"]],
               "ManualScoreMcam",
               "All")
  
nrow(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Zero"]]))               

analyzeResults(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["One"]]) %>%
                  dplyr::mutate(All = "All"),
               mcamKDmodel2_85[["fittedModels"]][["extraTreesOne"]],
               "ManualScoreMcam",
               "All")

nrow(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["One"]]))

analyzeResults(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]) %>%
                  dplyr::mutate(All = "All"),
               mcamKDmodel2_85[["fittedModels"]][["extraTreesTwo"]],
               "ManualScoreMcam",
               "All")

nrow(metricsScaled.MCAM.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]))
```

Sensitivity and specificity for each iteration when gbm and extraTrees classifiers are combined (Supp. Figure S7A, Figure 5D):
```{r}
# Iterations with combined classifier
metricsCleanMcamOtherMcam488.Classified.Zero <- classifyCleanMetricsCombinedModels(metricsCleanMcamOtherMcam488.Classified.Filt, metricsScaled.MCAM.Filt,
                                                                                   mcamKDmodel2_85[["fittedModels"]][["gbmZero"]], mcamKDmodel2_85[["fittedModels"]][["extraTreesZero"]],
                                                                                   "comboGbmExtraZero_MCAM2")
analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Zero %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Zero"]]) %>%
                  dplyr::mutate(All = "All"),
                "comboGbmExtraZero_MCAM2", "ManualScoreMcam", "All")

metricsCleanMcamOtherMcam488.Classified.One <- classifyCleanMetricsCombinedModels(metricsCleanMcamOtherMcam488.Classified.Filt, metricsScaled.MCAM.Filt,
                                                                                   mcamKDmodel2_85[["fittedModels"]][["gbmOne"]], mcamKDmodel2_85[["fittedModels"]][["extraTreesOne"]],
                                                                                   "comboGbmExtraOne_MCAM2")

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.One %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["One"]]) %>%
                  dplyr::mutate(All = "All"),
                "comboGbmExtraOne_MCAM2", "ManualScoreMcam", "All")

# Check:
metricsCleanMcamOtherMcam488.Classified.Two <- classifyCleanMetricsCombinedModels(metricsCleanMcamOtherMcam488.Classified.Filt, metricsScaled.MCAM.Filt,
                                                                                   mcamKDmodel2_85[["fittedModels"]][["gbmTwo"]], mcamKDmodel2_85[["fittedModels"]][["extraTreesTwo"]],
                                                                                   "comboGbmExtraTwo_MCAM2_Test")

identical(metricsCleanMcamOtherMcam488.Classified.Two %>% dplyr::select(-comboGbmExtraTwo_MCAM2) %>% rename(comboGbmExtraTwo_MCAM2 = comboGbmExtraTwo_MCAM2_Test),
          metricsCleanMcamOtherMcam488.Classified.Filt)

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]) %>%
                  dplyr::mutate(All = "All"),
                "comboGbmExtraTwo_MCAM2", "ManualScoreMcam", "All") 
```


Classifier with Haralick features produces low sensitivity
```{r}
mcamKDmodel1_85 <- readRDS(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/ClassifiersForMcam/modelList20221104_85up", sep = ""))
metricsCleanMcamOtherMcam488.Classified.Two.Texture <- classifyCleanMetricsCombinedModels(metricsCleanMcamOtherMcam488.Classified.Filt, metricsScaled.MCAM.Filt,
                                                                                   mcamKDmodel1_85[["fittedModels"]][["gbmTwo"]], mcamKDmodel1_85[["fittedModels"]][["extraTreesTwo"]],
                                                                                   "comboGbmExtraTwo_MCAM1")

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Two.Texture %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel1_85[["trainingSets"]][["Two"]]) %>%
                  dplyr::mutate(All = "All"),
                "comboGbmExtraTwo_MCAM1", "ManualScoreMcam", "All")

nrow(metricsCleanMcamOtherMcam488.Classified.Two.Texture %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel1_85[["trainingSets"]][["Two"]]))

metricsCleanMcamOtherMcam488.Classified.One.Texture <- classifyCleanMetricsCombinedModels(metricsCleanMcamOtherMcam488.Classified.Filt, metricsScaled.MCAM.Filt,
                                                                                   mcamKDmodel1_85[["fittedModels"]][["gbmOne"]], mcamKDmodel1_85[["fittedModels"]][["extraTreesOne"]],
                                                                                   "comboGbmExtraOne_MCAM1")

metricsCleanMcamOtherMcam488.Classified.Zero.Texture <- classifyCleanMetricsCombinedModels(metricsCleanMcamOtherMcam488.Classified.Filt, metricsScaled.MCAM.Filt,
                                                                                   mcamKDmodel1_85[["fittedModels"]][["gbmZero"]], mcamKDmodel1_85[["fittedModels"]][["extraTreesZero"]],
                                                                                   "comboGbmExtraZero_MCAM1")

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.One.Texture %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel1_85[["trainingSets"]][["One"]]) %>%
                  dplyr::mutate(All = "All"),
                "comboGbmExtraOne_MCAM1", "ManualScoreMcam", "All")

nrow(metricsCleanMcamOtherMcam488.Classified.One.Texture %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel1_85[["trainingSets"]][["One"]]))

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Zero.Texture %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel1_85[["trainingSets"]][["Zero"]]) %>%
                  dplyr::mutate(All = "All"),
                "comboGbmExtraZero_MCAM1", "ManualScoreMcam", "All")

nrow(metricsCleanMcamOtherMcam488.Classified.Zero.Texture %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel1_85[["trainingSets"]][["Zero"]]))
```

Check rounds of upSample by condition
```{r}
analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Zero %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Zero"]]),
                "comboGbmExtraZero_MCAM2", "ManualScoreMcam", "mainCondition")

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.One %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["One"]]),
                "comboGbmExtraOne_MCAM2", "ManualScoreMcam", "mainCondition")

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Two %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]) %>%
                  dplyr::mutate(All = "All"),
                "comboGbmExtraTwo_MCAM2", "ManualScoreMcam", "mainCondition")
```

Check accuracy of final iteration classifier for conditions and replicates:
```{r}
# Check:
analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Two %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]), 
                "comboGbmExtraTwo_MCAM2_Test", "ManualScoreMcam", "experimentGroup") 

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]), 
                "comboGbmExtraTwo_MCAM2", "ManualScoreMcam", "experimentGroup") 

metricsCleanMcamOtherMcam488.Classified.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]) %>% count(experimentGroup)

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]), 
                "comboGbmExtraTwo_MCAM2", "ManualScoreMcam", "mainRep") 

metricsCleanMcamOtherMcam488.Classified.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]) %>% count(mainRep)

analyzeResults2(metricsCleanMcamOtherMcam488.Classified.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]), 
                "comboGbmExtraTwo_MCAM2", "ManualScoreMcam", "mainCondition") 

metricsCleanMcamOtherMcam488.Classified.Filt %>%
                  merge(manualScoring %>% dplyr::select(Object, ManualScoreMcam, ConfidenceMcam), by = "Object") %>%
                  filter(!Object %in% mcamKDmodel2_85[["trainingSets"]][["Two"]]) %>% count(mainCondition)
```

Variable importance
```{r}
impGbm <- varImp(mcamKDmodel2_85[["fittedModels"]][["gbmTwo"]])
impExtra <- varImp(mcamKDmodel2_85[["fittedModels"]][["extraTreesTwo"]])

# write.csv(impGbm[["importance"]], paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/gbmImportantFeatures.csv", sep = ""))
# write.csv(impExtra[["importance"]], paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/extraTreesImportantFeatures.csv", sep = ""))
```

Feature importance violin plots (Supp. Fig. S7)
```{r}
# Looked at importance of features (overall for gbm or for the "OneEnd" class for extraTrees)
importantFeatures <- c("firstQuartileDistCentr2Wramp_MCAM", "medianIntensityWramp_MCAM", "brightPixWrampHalf_MCAM", "medianDistCentr2Wramp_MCAM", "medianWrampOverNot_MCAM", "areaWramp_MCAM") # First quartile distance was the most important for all classifiers except CRISPR extraTrees (still top 10). medianDst was second most important for KD classifiers, medianIntensityWramp was thrid most important for KD classifiers (still top 10 for CRISPR), brightPixWrampHalf" wass most important for extraTrees CRISPR (top 10 for gbm CRISPR). "medianWrampOverNot" - 4th most important for extraTrees, "areaWramp" - 4th most important for gbm

impMetricsKD <- metricsScaled.MCAM.Filt %>%
  dplyr::select(all_of(importantFeatures), Object) %>%
  merge(metricsCleanMcamOtherMcam488.Classified.Filt %>% dplyr::select(Object, comboGbmExtraTwo_MCAM2), by = "Object") %>%
  arrange(Object) 
identical(metricsCleanMcamOtherMcam488.Classified.Filt$Object, impMetricsKD$Object)
identical(metricsCleanMcamOtherMcam488.Classified.Filt$comboGbmExtraTwo_MCAM2, impMetricsKD$comboGbmExtraTwo_MCAM2)

# Sample size
impMetricsKD %>% count(comboGbmExtraTwo_MCAM2)

clr = c("OneEnd" = "#e66101", "BothEnds" = "#b2abd2", "None" = "#5e3c99")
for(val in 1:6){
  p <- ggplot(impMetricsKD %>% rename(Feature = importantFeatures[val]), aes(x = comboGbmExtraTwo_MCAM2, y = Feature, color = comboGbmExtraTwo_MCAM2)) + 
    geom_violin(draw_quantiles= c(0.25,0.5,0.75),
                width = 1.6,
                alpha = 1,
                scale = "count",
                trim = F,
                size = 1.2) +
    theme_classic() +
    ggtitle(importantFeatures[val]) +
    xlab("") +
    scale_color_manual(values = clr) +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 90, hjust = 1),
          legend.position = "none",
          title = element_text(size = 13),
          axis.title.y = element_text(size = 20),
          axis.text = element_text(size = 20))
  
  print(p)
  # ggsave(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/FeatureFigures/",
  #            importantFeatures[val], ".svg", sep = ""), plot = p, width = 12, height = 15, units = "cm", dpi = 600)
}
```

Feature distribution based on manual scoring (Fig. 5B)
```{r}
metricsPlotMan <- merge(metricsCleanMcamOtherMcam488.Classified.Filt, manualScoring %>% dplyr::select(ManualScoreMcam, Object), by = "Object") %>%
  dplyr::mutate(wramp = ifelse(ManualScoreMcam == "OneEnd", "OneEnd", "None")) %>%
  dplyr::mutate(wramp = factor(wramp,  c("OneEnd", "None")),
                ManualScoreMcam = factor(ManualScoreMcam, c("OneEnd", "BothEnds", "None")))

metricsPlotMan %>% group_by(wramp) %>% count(ManualScoreMcam) %>% ungroup()
nrow(metricsPlotMan) == nrow(manualScoring)

# Sample ssize
metricsPlotMan %>% count(wramp)

clr = c("OneEnd" = "#e66101", "BothEnds" = "#b2abd2", "None" = "#5e3c99")

ggplot(metricsPlotMan, aes(x = wramp, y = medianDistCentr2Wramp_MCAM, color = wramp)) + 
    geom_violin(draw_quantiles= c(0.25,0.5,0.75),
                width = 1.4,
                alpha = 1,
                scale = "count",
                trim = F,
                size = 1.2) +
    theme_classic() +
    ggtitle("Median Distance \nto Brightest Object") +
    ylab("Distance (pixels)")+
    xlab("") +
    scale_color_manual(values = clr) +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 90, hjust = 1),
          legend.position = "none",
          title = element_text(size = 13),
          axis.title.y = element_text(size = 20),
          axis.text = element_text(size = 20))
# ggsave(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/FeatureFigures/medianDistCentr2Wramp_Manual_2Class", ".svg", sep = ""), width = 12, height = 15, units = "cm", dpi = 600)

ggplot(metricsPlotMan, aes(x = ManualScoreMcam, y = medianDistCentr2Wramp_MCAM, color = ManualScoreMcam)) + 
    geom_violin(draw_quantiles= c(0.25,0.5,0.75),
                width = 1.4,
                alpha = 1,
                scale = "count",
                trim = F,
                size = 1.2) +
    theme_classic() +
    ggtitle("Median Distance \nto Brightest Object") +
    ylab("Distance (pixels)")+
    xlab("") +
    scale_color_manual(values = clr) +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 90, hjust = 1),
          legend.position = "none",
          title = element_text(size = 13),
          axis.title.y = element_text(size = 20),
          axis.text = element_text(size = 20))
# ggsave(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/FeatureFigures/medianDistCentr2Wramp_Manual_3Class", ".svg", sep = ""), width = 12, height = 15, units = "cm", dpi = 600)
```

Boxplots of texture features (Supp. Fig. 6D)
```{r}
plots1scaleV2 <- function(featureNames, data, chName, savePath, logOption){
  features <- str_replace(featureNames, "MCAM", chName)
  for(val in 1:length(features)){
  p <- ggplot(data %>% rename(feature = features[val])) +
    geom_jitter(aes(x=Coverslip, y = feature, color = experimentGroup), height = 0, alpha = 0.4, size = 0.5) +
    geom_boxplot(aes(x=Coverslip, y = feature, fill = experimentGroup), alpha = 0, outlier.size = .5) +
    ggtitle(features[val])+
    theme_classic() +
    theme(text = element_text(size = 13)) +
    theme(axis.text.x= element_text(size = 6, angle = 90, hjust = 1))
 
  # ggsave(paste(savePath, features[val], "_expGroup.png", sep = ""), p, width = 7.5, height = 5, dpi = 600)
 
  if(logOption == T){
      p <- ggplot(data %>% rename(feature = features[val])) +
        geom_jitter(aes(x=Coverslip, y = log(feature), color = experimentGroup), height = 0, alpha = 0.4, size = 0.5) +
        geom_boxplot(aes(x=Coverslip, y = log(feature), fill = experimentGroup), alpha = 0, outlier.size = .5) +
        ggtitle(paste(features[val], "- Log"))+
        theme_classic() +
        theme(text = element_text(size = 13)) +
        theme(axis.text.x= element_text(size = 6, angle = 90, hjust = 1))
   
      # ggsave(paste(savePath, features[val], "_log_expGroup.png", sep = ""), p, width = 7.5, height = 5, dpi = 600)
    }
  }
}

plots1scaleV2(colnames(metricsScaled.MCAM.Filt %>% dplyr::select(contains("Texture"))),
              metricsScaled.MCAM.Filt,
              "MCAM",
              paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/TexturePlots/", sep = ""), F)

# Sample size
numPerCoverslip <- metricsScaled.MCAM.Filt %>% count(Coverslip)
numPerCoverslip
sum(numPerCoverslip$n)
min(numPerCoverslip$n)
max(numPerCoverslip$n)
```

Compile supplemental data: compiled feature data, manual annotation for ML, and results of copolarization analysis:
```{r}
copolarizationLabeled <- read.csv(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/copolarizationLabeled.csv", sep = "")) # From Polarized Cells Figures notebook

# Features for supplemental table:
featuresMcamAll <- read.csv(paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/InputForML/SupplementalMcamFeatures.csv", sep=""))

suppFeatures2 <- c("Object", "comboGbmExtraTwo_MCAM2", "ManualScoreMcam", "WrongObject", "copolarOther", "copolarFactin", "copolarTriple","experimentGroup", "Experiment", "Image", "stain", "mainCondition", "Condition", "mainRep", "Replicate", "Coverslip", featuresMcamAll$Feature)

suppMetricsAll <- metricsCleanMcamOtherMcam488.Classified.Filt %>%
  merge(manualScoring %>% dplyr::select(ManualScoreMcam, Object, WrongObject), by="Object", all.x = T) %>%
  dplyr::mutate(stain = str_remove(Condition, ".*Stain")) %>%
  dplyr::mutate(stain = str_remove(stain, "_KD.*")) %>%
  merge(copolarizationLabeled %>% dplyr::select(Object, copolarOther, copolarFactin, copolarTriple), all.x = T, all.y = T, by = "Object") %>%
  dplyr::select(all_of(suppFeatures2)) %>%
  dplyr::rename(Classification = comboGbmExtraTwo_MCAM2)

# No copolarization scoring for radixin included
suppMetricsAll %>% filter(str_detect(Condition, "StainMCAM-RDX")) %>% count(copolarOther)
suppMetricsAll %>% filter(str_detect(Condition, "StainMCAM-RDX")) %>% count(copolarFactin)
suppMetricsAll %>% filter(str_detect(Condition, "StainMCAM-RDX")) %>% count(copolarTriple)

suppMetricsAll %>% count(ManualScoreMcam)
manualScoring %>% filter(Object %in% metricsCleanMcamOtherMcam488.Classified.Filt$Object) %>% count(ManualScoreMcam)

# Check preservation of metrics data
identical(suppMetricsAll %>% dplyr::rename(comboGbmExtraTwo_MCAM2 = Classification) %>% dplyr::select(all_of(setdiff(suppFeatures2, c("copolarOther", "copolarFactin", "copolarTriple", "stain", "ManualScoreMcam", "WrongObject")))) %>% arrange(Object),
          metricsCleanMcamOtherMcam488.Classified.Filt %>% dplyr::select(all_of(setdiff(suppFeatures2, c("copolarOther", "copolarFactin", "copolarTriple", "stain", "ManualScoreMcam", "WrongObject")))) %>% arrange(Object))

suppMetricsAll2 <- suppMetricsAll %>% dplyr::select(-Experiment) %>% dplyr::rename(Experiment = experimentGroup) %>% arrange(Object)

identical(suppMetricsAll2 %>% dplyr::select(-Experiment), suppMetricsAll %>% arrange(Object) %>% dplyr::select(-Experiment, -experimentGroup))
unique(suppMetricsAll2$Condition)
unique(suppMetricsAll2$Experiment)
unique(suppMetricsAll2$stain)

nrow(suppMetricsAll2) == nrow(metricsCleanMcamOtherMcam488.Classified.Filt)

setdiff(featuresMcamAll$Feature, colnames(suppMetricsAll2))

write_csv(suppMetricsAll2, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/SupplementalData_ClassifiedAllMcamMetrics2.csv", sep = ""))
```

Supplemental data: scaled features
```{r}
metricsScaled.MCAM.Supp <- metricsScaled.MCAM.Filt %>%
  dplyr::select(-Normalization, -Experiment) %>%
  dplyr::rename(Experiment = experimentGroup) %>%
  filter(Object %in% metricsCleanMcamOtherMcam488.Classified.Filt$Object) %>%
  arrange(Object)

nrow(metricsScaled.MCAM.Supp) == nrow(metricsCleanMcamOtherMcam488.Classified.Filt)
identical(metricsScaled.MCAM.Supp$Object, suppMetricsAll2$Object)
unique(metricsScaled.MCAM.Supp$Condition)
unique(metricsScaled.MCAM.Supp$Replicate)
unique(metricsScaled.MCAM.Supp$mainCondition)
unique(metricsScaled.MCAM.Supp$Experiment)

write_csv(metricsScaled.MCAM.Supp, paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/SupplementalData_ScaledFeaturesMcam2.csv", sep = ""))

# Objects in final training set
write.csv(mcamKDmodel2_85[["trainingSets"]][["Two"]], paste(dirPath, "AllReplicatesAnalysisInR/AllReplicates_RevisedAnalysis_20221101/Output/SupplementalData_FinalTrainingSet2.csv", sep = ""))
length(mcamKDmodel2_85[["trainingSets"]][["Two"]])
```

