---
title: "BioID Analysis"
output: html_notebook
---

This notebook contains the analyses/figures of the BioID data from the paper. 

Here, the MaxQuant output was loaded, and feature data from the evidence file was rolled up into protein quantitation using the groupings in the protein groups file. A custom script was used to roll up the data, such that all peptides were summed per protein (i.e., shared peptides were used more than once).

Technical replicates were summed and then formatted for SAINT analysis of spectral counts and Perseus analysis of median-normalized intensities. The output from SAINT and Perseus were then loaded into this notebook and plotted.

```{r}
R.Version() # Version 4.3.0
RStudio.Version() # Version 1.4.1717

library(tidyverse)
library(readxl)
library(gridExtra)
library(ggbeeswarm)
```

Path to directory:
```{r}
dirPath <- "/Your/Directory/Path/"
```

Input data:
```{r}
# MaxQuant output
evidence <- read.delim(paste(dirPath, "CCE20220123_Suzannah_Miller_MCAM_BioID/evidence.txt", sep = ""))

proteinGroups <- read.delim(paste(dirPath, "CCE20220123_Suzannah_Miller_MCAM_BioID/proteinGroups.txt", sep = "")) %>%
  arrange(Majority.protein.IDs)

# User-made annotation file which facilitates formatting for SAINT
annotation <- read_excel(paste(dirPath, "MassSpecAnalysis/20211101BioID_Annotation.xlsx", sep = "")) %>%
  mutate(reprintBait1 = ifelse(T.C.label.v1 == "T", Bait.v1, "CONTROL")) %>%
  mutate(reprintBait2 = ifelse(T.C.label.v2 == "T", Bait.v2, "CONTROL")) %>%
  arrange(Sample.name)
head(annotation)
```

Functions for rolling features into protein-level data, where all peptides are summed for each proteinGroup (including shared peptides) or razor peptides are summed.
```{r}
rollupAll <- function(proteinGroupsdf, evidencedf){
  for(val1 in 0:nrow(proteinGroupsdf)) {
    tempRow <- filter(proteinGroupsdf, id == val1)
    evidIdx <- str_split(tempRow$Evidence.IDs, ";", simplify = T)
    evidForProteinGroup <- filter(evidencedf, id %in% evidIdx) 
    evidForProteinGroup <- mutate(evidForProteinGroup, 
           MS.MS.count = ifelse(Type == "MULTI-SECPEP", 0, MS.MS.count))
    tempSpcAll <- evidForProteinGroup %>%
      group_by(Raw.file, .drop = F) %>%
      summarize(spc = sum(MS.MS.count, na.rm = T), intensity = sum(Intensity, na.rm = T)) %>%
      mutate(Majority.protein.IDs = tempRow$Majority.protein.IDs, 
             Gene.names = tempRow$Gene.names,
             Sequence.length = tempRow$Sequence.length,
             Protein.names = tempRow$Protein.names, 
             Only.identified.by.site = tempRow$Only.identified.by.site, 
             Reverse = tempRow$Reverse, 
             Potential.contaminant = tempRow$Potential.contaminant)
    if(val1 == 0){
      spcProteinsAll = tempSpcAll
    } else {
      spcProteinsAll <- rbind(spcProteinsAll, tempSpcAll)
    }
  }
  return(spcProteinsAll)
}

rollupRazor <- function(proteinGroupsdf, evidencedf){
  for(val1 in 0:nrow(proteinGroupsdf)) {
    tempRow <- filter(proteinGroupsdf, id == val1)
    evidIdx <- str_split(tempRow$Evidence.IDs, ";", simplify = T)
    evidForProteinGroup <- filter(evidencedf, id %in% evidIdx) 
    evidForProteinGroup <- mutate(evidForProteinGroup, 
           MS.MS.count = ifelse(Type == "MULTI-SECPEP", 0, MS.MS.count))
    majProtId <- str_split(tempRow$Majority.protein.IDs, ";", simplify = T)
    razorIdx <- which(evidForProteinGroup$Leading.razor.protein == majProtId[1])
    tempSpcRazor <- evidForProteinGroup[razorIdx,] %>%
      group_by(Raw.file, .drop = F) %>%
      summarize(spc = sum(MS.MS.count, na.rm = T), intensity = sum(Intensity, na.rm = T)) %>%
      mutate(Majority.protein.IDs = tempRow$Majority.protein.IDs, 
             Gene.names = tempRow$Gene.names,
             Sequence.length = tempRow$Sequence.length,
             Protein.names = tempRow$Protein.names, 
             Only.identified.by.site = tempRow$Only.identified.by.site, 
             Reverse = tempRow$Reverse,
             Potential.contaminant = tempRow$Potential.contaminant)
    if(val1 == 0){
      spcProteinsRazor = tempSpcRazor
    } else {
      spcProteinsRazor <- rbind(spcProteinsRazor, tempSpcRazor)
    }
  }
  return(spcProteinsRazor)
}
```

Functions to format for Perseus or SAINT analysis:
```{r}
# Format for MaxQuant
formatForMaxQuant <- function(data, measurement){
  wide <- data %>%
    rename(metric = measurement) %>%
    select(BiologicalReplicate, Majority.protein.IDs, Gene.names, metric) %>%
    spread(key = BiologicalReplicate, value = metric, fill = 0)
}

# Format for SAINT
formatForReprint <- function(proteinData, annotationdf){
  reprintInfoCols <- proteinData %>%
    select(Majority.protein.IDs, Gene.names, Sequence.length, Protein.names) %>%
    rename(PROTID = Majority.protein.IDs,
           GENEID = Gene.names,
           PROTLEN = Sequence.length,
           DEFLINE = Protein.names) %>%
    mutate(PROTID = str_extract(PROTID, regex('[^;]*')),
           GENEID = str_extract(GENEID, regex('[^;]*')))
  
  dataLong <- proteinData %>%
    select(Majority.protein.IDs, all_of(annotationdf$BiologicalReplicate)) %>%
    gather(key = BiologicalReplicate, value = "Value", annotationdf$BiologicalReplicate)  %>%
    select(Majority.protein.IDs, BiologicalReplicate, Value) %>%
    rename(PROTID = Majority.protein.IDs) %>%
    mutate(PROTID = str_extract(PROTID, regex('[^;]*')))

  # Create matrix format for SAINT
  dataWide = dataLong %>%
    spread(key = BiologicalReplicate, value = Value, fill = NA, drop = FALSE)
  reprintWide = merge(reprintInfoCols, dataWide, by = "PROTID")
  
  # Check for unique PROTIDs (should be TRUE)
  print("Unique PROTIDs?")
  print(length(reprintWide$PROTID) == length(unique(reprintWide$PROTID)))
  print("nrow(input) == nrow(reprintMatrix)?")
  print(nrow(reprintWide) == nrow(proteinData))

  # Check that reformatting kept original values
  proteinGroupsTemp <- proteinData %>%
    select(Majority.protein.IDs, all_of(annotationdf$BiologicalReplicate)) %>%
    rename(PROTID = Majority.protein.IDs) %>%
    mutate(PROTID = str_extract(PROTID, regex('[^;]*'))) %>%
    arrange(PROTID)
  for (val in 1:nrow(annotationdf)){
    print(paste('Values Preserved for', annotationdf$BiologicalReplicate[val]))
    print(all(select(proteinGroupsTemp, all_of(annotationdf$BiologicalReplicate[val])) == select(reprintWide, all_of(annotationdf$BiologicalReplicate[val]))))
  }
  remove(proteinGroupsTemp)
  return(reprintWide)
}

header <- function(reprintWide, annotationdf, reprintBaitName, option){
  annotationTemp <- select(annotationdf, BiologicalReplicate, reprintBaitName) %>%
    rename(reprintBait = reprintBaitName)
  headersTemp <- data.frame(firstRow = colnames(reprintWide)) %>%
    mutate(secondRow = firstRow)
  headersTemp2 <- headersTemp
  for (val in 1:nrow(headersTemp)){
    if (headersTemp$secondRow[val] %in% annotationTemp$BiologicalReplicate){
    idx = which(annotationTemp$BiologicalReplicate == headersTemp$secondRow[val])
    headersTemp2$secondRow[val] <- annotationTemp$reprintBait[idx]
    }
  }
  headersTemp2 <- mutate(headersTemp2, firstRow = ifelse(firstRow %in% annotationTemp$BiologicalReplicate, paste(firstRow, option, sep = "_"), firstRow))
  headers <- as_tibble(t(headersTemp2))
}
```

Roll up all peptides per protein (using shared peptides more than once).
```{r}
evidence2 <- evidence %>%
  filter(!str_detect(Raw.file, "s4"), !str_detect(Raw.file, "s9")) # Remove samples in the MaxQuant search which were not included in this study.

proteinsAll2 <- rollupAll(proteinGroups, evidence2)
```

Roll up unfiltered razor peptides and compare to proteinGroups to check roll-up function:
```{r}
proteinsRazorNorm <- rollupRazor(proteinGroups, evidence)
proteinsRazorSpcWide <- merge(proteinsRazorNorm, select(annotation, ProteinGroups, Raw.file), by = "Raw.file") %>%
  select(-Raw.file, -intensity) %>%
  spread(key = "ProteinGroups", value = "spc", fill = 0) %>%
  arrange(Majority.protein.IDs)

# Spectral counts are identical
pg <- proteinGroups %>% dplyr::select(Majority.protein.IDs, contains("MS.MS.count."))
identical(pg$Majority.protein.IDs, proteinsRazorSpcWide$Majority.protein.IDs)
columnNames <- colnames(proteinsRazorSpcWide)
columnNamesPg <- colnames(pg)
for(val in 1:26){
  x <- proteinsRazorSpcWide[which(str_detect(columnNames, annotation$ProteinGroups[val]))]
  y <- pg[which(str_detect(columnNamesPg, annotation$ProteinGroups[val]))] %>%
    dplyr::mutate_all(as.numeric)
  if(identical(x[,],y[,]) == F){
    print(paste(annotation$ProteinGroups[val], "is not identical"))
  }
}

# Intensities are not identical, but it appears like rounding differences
proteinsRazorIntensityWide <- merge(proteinsRazorNorm, select(annotation, ProteinGroups, Raw.file), by = "Raw.file") %>%
  select(-Raw.file, -spc) %>%
  spread(key = "ProteinGroups", value = "intensity", fill = 0) %>%
  arrange(Majority.protein.IDs)
pg <- proteinGroups %>% dplyr::select(Majority.protein.IDs, contains("Intensity."), -contains("LFQ"))
identical(pg$Majority.protein.IDs, proteinsRazorIntensityWide$Majority.protein.IDs)
columnNames <- colnames(proteinsRazorIntensityWide)
columnNamesPg <- colnames(pg)
for(val in 1:26){
  x <- proteinsRazorIntensityWide[which(str_detect(columnNames, annotation$ProteinGroups[val]))]
  y <- pg[which(str_detect(columnNamesPg, annotation$ProteinGroups[val]))] %>%
    dplyr::mutate_all(as.numeric)
  print(plot(x[,],y[,]))
}
```

Combine (sum) technical replicates to give values for each biological replicate, using the sum of all peptides per protein group (e.g., double-dipping), and divide by the number of iBAQ peptides:
```{r}
proteinIntensitiesBio <- proteinsAll2 %>% 
    filter(intensity != 0)%>%
    merge(proteinGroups %>% select(Majority.protein.IDs, Protein.IDs, iBAQ.peptides), by = "Majority.protein.IDs") %>%
    merge(annotation %>% select(BiologicalReplicate, Condition, Sample.name, Raw.file), by = "Raw.file") %>%
    filter(Potential.contaminant != "+", Reverse != "+") %>% 
    mutate(iBAQ = intensity/iBAQ.peptides) %>%
    group_by(Condition, BiologicalReplicate, Protein.IDs, Majority.protein.IDs, Gene.names) %>%
    summarize(intensity = sum(intensity, na.rm = T),
              iBAQ = sum(iBAQ, na.rm = T),
              spc = sum(spc, na.rm = T)) %>%
    ungroup()

sum(is.na(proteinIntensitiesBio$iBAQ)) # No missing values
```

Median normalize intensities
```{r}
# Global median (median of medians)
medianIntensities <- proteinIntensitiesBio %>% group_by(BiologicalReplicate) %>% summarize(median = median(iBAQ), sum = sum(iBAQ)) %>% ungroup()
ggplot(medianIntensities, aes(x = median, y = sum)) + geom_point()
globalMedian <- median(medianIntensities$median)

# Normalize the data
proteinIntensitiesBioNorm <-proteinIntensitiesBio %>%
  group_by(BiologicalReplicate) %>%
  mutate(iBAQnorm = iBAQ/median(iBAQ)*globalMedian) %>%
  ungroup()

# Check raw values preserved
nrow(proteinIntensitiesBio) == nrow(proteinIntensitiesBioNorm)
identical(proteinIntensitiesBio$Majority.protein.IDs, proteinIntensitiesBioNorm$Majority.protein.IDs)
identical(proteinIntensitiesBio$intensity, proteinIntensitiesBioNorm$intensity)

# Check medians are identical
proteinIntensitiesBioNorm %>% group_by(BiologicalReplicate) %>% summarize(median(iBAQnorm)) %>% ungroup()

# Save normalized data
write_csv(proteinIntensitiesBioNorm, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Perseus20230512/proteinIntensitiesMedianNormalized_Test.csv", sep = ""))
```

Violin plots and boxplots of intensities (Supplemental Figure):
```{r}
# Fix order of plots
repLevels <- c("McamBiraA", "McamBiraB", "McamBiraC", "LynBiraA", "LynBiraB", "LynBiraC", "BiraNesB", "BiraNesC", "NoneA", "NoneB", "NoneC", "McamBiraROCKiB", "McamBiraROCKiC")

ggplot(proteinIntensitiesBioNorm %>%
         mutate(BiologicalReplicate = factor(BiologicalReplicate, levels = repLevels)), 
       aes(x = BiologicalReplicate, y = log2(iBAQ), color = Condition)) +
    geom_beeswarm(alpha = 0.2, cex = .3, size = .5) +
  geom_boxplot(alpha = .6, width = 0.5, size = 1, color = "black") + 
  ggtitle("Norm Filtered Human Protein Intensities - All Peptides")  +
  ylab("Log2(iBAQ)") +
  theme_classic() +
  scale_y_continuous(breaks = seq(5,30,5)) +
  theme(text = element_text(size = 13),
        axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size = 14))
# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/ReplicatePlots/ProteinIbaqAllPeptides_BeforeMedianNorm_Boxplot.svg", sep = ""), width = 5, height = 3, units = "in", dpi = 600)

ggplot(proteinIntensitiesBioNorm %>%
         mutate(BiologicalReplicate = factor(BiologicalReplicate, levels = repLevels)), 
       aes(x = BiologicalReplicate, y = log2(iBAQnorm), color = Condition)) +
    geom_beeswarm(alpha = 0.2, cex = .3, size = .5) +
  geom_boxplot(alpha = .6, width = 0.5, size = 1, color = "black") + 
  ggtitle("Norm Filtered Human Protein Intensities - All Peptides")  +
  ylab("Log2(iBAQ)") +
  theme_classic() +
  scale_y_continuous(breaks = seq(5,30,5)) +
  theme(text = element_text(size = 13),
        axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size = 14))
# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/ReplicatePlots/ProteinIbaqAllPeptides_AfterMedianNorm_Boxplot.svg", sep = ""), width = 5, height = 3, units = "in", dpi = 600)
```

Plots of average spectral counts or intensities comparing constructs (Supplemental Figure):
```{r}
lm_condition <- function(dataSum, condition1, condition2, xEqn, yEqn, measurement, title, axLab1, axLab2){
  proteinsWide <- dataSum %>%
    select(Condition, Majority.protein.IDs, all_of(measurement)) %>%
    rename(intensity = measurement) %>%
    filter(intensity != 0) %>%
    mutate(intensity = log2(intensity)) %>%
    mutate(intensity = ifelse(is.infinite(intensity), NA, intensity)) %>%
    group_by(Condition, Majority.protein.IDs) %>%
    summarize(meanIntensity = mean(intensity, na.rm = T)) %>%
    ungroup() %>%
    spread(key = Condition, value = meanIntensity, fill = NA) %>%
        rename(xVar = condition1,
            yVar = condition2)
  
    df <- proteinsWide %>% dplyr::select(Majority.protein.IDs, xVar, yVar)

m <- lm(yVar ~ xVar, df, na.action = na.exclude)
    eq <- paste('y = ', format(unname(coef(m)[1]), digits = 2), ' + ', format(unname(coef(m)[2]), digits = 2), 'x    R^2 = ', ... = format(summary(m)$r.squared, digits = 3), sep = "")

  p1 = ggplot(df %>% mutate(xVar = ifelse(is.na(xVar), -Inf, xVar),
                            yVar = ifelse(is.na(yVar), -Inf, yVar)), 
              aes(x = xVar, y = yVar)) + geom_point(alpha = 0.4, size = 1) +
     #geom_point(data = df %>% filter(Majority.protein.IDs %in% c("P26038", "E7EQR4;P15311", "P35241;A0A2R8Y5S7;A0A2R8Y7M3")), aes(x = xVar, y = yVar, color = Majority.protein.IDs)) +
          geom_abline(slope = coef(m)[[2]], intercept = coef(m)[[1]]) +
          geom_text(x = xEqn, y = yEqn, label = eq, size = 3.5) +
          theme_classic() +
          ylab(axLab2) + xlab(axLab1) +
    ggtitle(title) +
    theme(text = element_text(size = 14),
          plot.title = element_text(size = 14))
  print(p1)
  # ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/ReplicatePlots/",condition1, "-", condition2, "_Mean_", measurement, "_Revised.png", sep = ""), width = 3, height = 3, units = "in", dpi = 600)
}

lm_condition(proteinIntensitiesBioNorm, "McamBira", "LynBira", 5, 11, "spc", "SPCs", "MCAM-BirA*-HA", "Lyn11-BirA*-HA")
lm_condition(proteinIntensitiesBioNorm, "McamBira", "BiraNes", 5, 9.5, "spc", "SPCs", "MCAM-BirA*-HA", "BirA*-HA-NES")
lm_condition(proteinIntensitiesBioNorm, "McamBira", "LynBira", 25, 36, "intensity", "Mean Intensity", "MCAM-BirA*-HA", "Lyn11-BirA*-HA")
lm_condition(proteinIntensitiesBioNorm, "McamBira", "BiraNes", 25, 36, "intensity", "Mean Intensity", "MCAM-BirA*-HA", "BirA*-HA-NES")

lm_condition(proteinIntensitiesBioNorm, "McamBira", "LynBira", 14, 26, "iBAQnorm", "Mean Norm iBAQ", "MCAM-BirA*-HA", "Lyn11-BirA*-HA")
lm_condition(proteinIntensitiesBioNorm, "McamBira", "BiraNes", 14, 26, "iBAQnorm", "Mean Norm iBAQ", "MCAM-BirA*-HA", "BirA*-HA-NES")

lm_condition(proteinIntensitiesBioNorm, "McamBira", "LynBira", 18.5, 29.5, "iBAQ", "Mean iBAQ", "MCAM-BirA*-HA", "Lyn11-BirA*-HA")
lm_condition(proteinIntensitiesBioNorm, "McamBira", "BiraNes", 18.5, 29.5, "iBAQ", "Mean iBAQ", "MCAM-BirA*-HA", "BirA*-HA-NES")
```

Format for SAINT
```{r}
# Sum biological replicates with PROTID as the first entry in Majority.protein.IDs from protein groups file
proteinsSpcBioSum <- merge(proteinsAll2, select(annotation, Sample.name, Raw.file, BiologicalReplicate), by = "Raw.file")  %>%
  filter(Reverse != "+") %>%
  filter(Only.identified.by.site != "+") %>%
  group_by(Majority.protein.IDs, Gene.names, Protein.names, Sequence.length, BiologicalReplicate) %>%
  summarize(spc = sum(spc)) %>%
  ungroup() %>%
  spread(key = "BiologicalReplicate", value = "spc", fill = 0) %>%
  arrange(Majority.protein.IDs)

reprintSpcAll <- formatForReprint(proteinsSpcBioSum, annotation %>% filter(!str_detect(ProteinGroups, "s4"), !str_detect(ProteinGroups, "s9")))
headerSpcAllControls <- header(reprintSpcAll, annotation %>% filter(!str_detect(ProteinGroups, "s4"), !str_detect(ProteinGroups, "s9")), "reprintBait1", "SPC")

# Get uniprot names for contaminants (by removing "CON__" from Majority.protein.IDs) and change MCAMBIRA to uniprot/HGNC
proteinsSpcBioSumRenamed <- merge(proteinsAll2, select(annotation, Sample.name, Raw.file, BiologicalReplicate), by = "Raw.file")  %>%
  filter(Reverse != "+") %>%
  filter(Only.identified.by.site != "+") %>%
  mutate(Majority.protein.IDs = str_remove_all(Majority.protein.IDs, "CON__ENSEMBL:")) %>%
  mutate(Majority.protein.IDs = str_remove_all(Majority.protein.IDs, "CON__")) %>%
  mutate(Majority.protein.IDs = ifelse(str_detect(Majority.protein.IDs, "P04259") & Gene.names != "KRT6B", "CON_P04259", Majority.protein.IDs)) %>%
  mutate(Majority.protein.IDs = str_remove_all(Majority.protein.IDs, "REFSEQ:")) %>%
  mutate(Majority.protein.IDs = ifelse(str_detect(Majority.protein.IDs, "MCAMBirA"), "P43121", Majority.protein.IDs)) %>%
  group_by(Majority.protein.IDs, Gene.names, Protein.names, Sequence.length, BiologicalReplicate) %>%
  summarize(spc = sum(spc)) %>%
  ungroup() %>%
  spread(key = "BiologicalReplicate", value = "spc", fill = 0) %>%
  arrange(Majority.protein.IDs)

reprintSpcAllRenamed <- formatForReprint(proteinsSpcBioSumRenamed, annotation %>% filter(!str_detect(ProteinGroups, "s4"), !str_detect(ProteinGroups, "s9")))

# Check differences to make sure renaming worked correctly:
setdiff(proteinsSpcBioSum, proteinsSpcBioSumRenamed)
setdiff(reprintSpcAll$PROTID, reprintSpcAllRenamed$PROTID)
setdiff(reprintSpcAll, reprintSpcAllRenamed)

# Remove nonhuman contaminants
contaminants <- proteinGroups %>% filter(Potential.contaminant == "+")  %>%
  mutate(firstID = str_extract(Majority.protein.IDs, regex('[^;]*'))) %>%
  mutate(Majority.protein.IDs.New = str_remove_all(Majority.protein.IDs, "CON__ENSEMBL:")) %>%
  mutate(Majority.protein.IDs.New = str_remove_all(Majority.protein.IDs.New, "CON__")) %>%
  mutate(Majority.protein.IDs.New = ifelse(str_detect(Majority.protein.IDs.New, "P04259") & Gene.names != "KRT6B", "CON_P04259", Majority.protein.IDs.New)) %>%
  mutate(Majority.protein.IDs.New = str_remove_all(Majority.protein.IDs.New, "REFSEQ:")) %>%
  mutate(Majority.protein.IDs.New = ifelse(str_detect(Majority.protein.IDs.New, "MCAMBirA"), "P43121", Majority.protein.IDs.New)) %>%
  mutate(firstIDnew = str_extract(Majority.protein.IDs.New, regex('[^;]*')))

proteinsSpcBioSumRenamedHumanCon <- merge(proteinsAll2, select(annotation, Sample.name, Raw.file, BiologicalReplicate), by = "Raw.file")  %>%
  filter(Reverse != "+") %>%
  filter(Only.identified.by.site != "+") %>%
  filter(!Majority.protein.IDs %in% contaminants$Majority.protein.IDs[!str_detect(contaminants$Fasta.headers, "HUMAN")]) %>%
  mutate(Majority.protein.IDs = str_remove_all(Majority.protein.IDs, "CON__ENSEMBL:")) %>%
  mutate(Majority.protein.IDs = str_remove_all(Majority.protein.IDs, "CON__")) %>%
  mutate(Majority.protein.IDs = ifelse(str_detect(Majority.protein.IDs, "P04259") & Gene.names != "KRT6B", "CON_P04259", Majority.protein.IDs)) %>%
  mutate(Majority.protein.IDs = str_remove_all(Majority.protein.IDs, "REFSEQ:")) %>%
  mutate(Majority.protein.IDs = ifelse(str_detect(Majority.protein.IDs, "MCAMBirA"), "P43121", Majority.protein.IDs)) %>%
  group_by(Majority.protein.IDs, Gene.names, Protein.names, Sequence.length, BiologicalReplicate) %>%
  summarize(spc = sum(spc)) %>%
  ungroup() %>%
  spread(key = "BiologicalReplicate", value = "spc", fill = 0) %>%
  arrange(Majority.protein.IDs)

reprintSpcAllRenamedHumanCon <- formatForReprint(proteinsSpcBioSumRenamedHumanCon, annotation %>% filter(!str_detect(ProteinGroups, "s4"), !str_detect(ProteinGroups, "s9")))

# Check differences to make sure renaming and removing nonhuman contaminants worked:
setdiff(proteinsSpcBioSum,proteinsSpcBioSumRenamedHumanCon) # 68
setdiff(proteinsSpcBioSumRenamed,proteinsSpcBioSumRenamedHumanCon) # 32
nrow(proteinGroups %>% filter(Potential.contaminant == "+", !str_detect(Fasta.headers, "HUMAN"))) # 32 nonhuman contaminants
nrow(proteinsSpcBioSum) - nrow(proteinsSpcBioSumRenamedHumanCon) # 32 rows removed

setdiff(reprintSpcAll$PROTID, reprintSpcAllRenamedHumanCon$PROTID) # 55
setdiff(reprintSpcAllRenamed$PROTID, reprintSpcAllRenamedHumanCon$PROTID) # 32
setdiff(reprintSpcAll, reprintSpcAllRenamedHumanCon)
sum(str_detect(reprintSpcAllRenamedHumanCon$PROTID, ";"))

contaminants %>% filter(!Majority.protein.IDs %in% contaminants$Majority.protein.IDs[str_detect(contaminants$Fasta.headers, "HUMAN")])
contaminants %>% filter(Majority.protein.IDs %in% contaminants$Majority.protein.IDs[str_detect(contaminants$Fasta.headers, "HUMAN")])
filter(contaminants, Majority.protein.IDs.New %in% proteinsSpcBioSumRenamedHumanCon$Majority.protein.IDs)  # 1 protein only identified by site was removed in addition to nonhuman contaminants
siteOnly <- filter(contaminants, Only.identified.by.site == "+")
filter(contaminants, !Majority.protein.IDs.New %in% proteinsSpcBioSumRenamedHumanCon$Majority.protein.IDs)  # 33 removed
nrow(reprintSpcAll) - nrow(reprintSpcAllRenamedHumanCon) # 32 because only identified by site was removed from both
filter(reprintSpcAll, PROTID == siteOnly$firstID)
filter(reprintSpcAllRenamedHumanCon, PROTID == siteOnly$firstID)
proteinsSpcBioSum %>% filter(Majority.protein.IDs == siteOnly$Majority.protein.IDs)

# Save file to upload to https://reprint-apms.org/
write.table(headerSpcAllControls, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Reprint20230505/Input/20220512_ReprintMatrixSpcAllPeptides_AllControls_RenamedPrey_HumanCon_Test.txt",sep = ""), append = FALSE, quote = FALSE, sep = "\t", col.names = FALSE, row.names = FALSE)
write.table(reprintSpcAllRenamedHumanCon, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Reprint20230505/Input/20220512_ReprintMatrixSpcAllPeptides_AllControls_RenamedPrey_HumanCon_Test.txt",sep = ""), append = TRUE, quote = FALSE, sep = "\t", col.names = FALSE, row.names = FALSE)
```

Remove low-confidence identifications before analysis in Perseus:
```{r}
# Remove proteins with <2X fold-change over no construct control (based on raw intensities)
fcMcamNoneBaq <- proteinIntensitiesBioNorm %>%
  select(Condition, BiologicalReplicate, Majority.protein.IDs, Gene.names, iBAQ) %>%
  mutate(iBAQ = log2(iBAQ)) %>%
  mutate(iBAQ = ifelse(is.infinite(iBAQ), NA, iBAQ)) %>%
  group_by(Condition, Majority.protein.IDs) %>%
  summarize(meaniBAQ = mean(iBAQ, na.rm = T)) %>%
  ungroup() %>%
  spread(key = Condition, value = meaniBAQ) %>%
  filter(!is.na(McamBira)) %>%
  mutate(fcMcamNone = McamBira - None) %>%
  mutate(fcMcamNone = ifelse(is.na(None), Inf, fcMcamNone)) %>%
  filter(fcMcamNone > 1)

# Remove proteins without at least 2 unique peptides in 2 technical replicates of MCAM-BirA* (DMSO)
proteinGroups2unique <- proteinGroups %>% 
  select(Majority.protein.IDs, Unique.peptides.s1_MCAM_BirA_DMSO_A1, Unique.peptides.s1_MCAM_BirA_DMSO_A2,
         Unique.peptides.s5_MCAM_BirA_DMSO_B1, Unique.peptides.s5_MCAM_BirA_DMSO_B2,
         Unique.peptides.s10_MCAM_BirA_DMSO_C1, Unique.peptides.s10_MCAM_BirA_DMSO_C1) %>%
  mutate_if(is.numeric, function(x){x > 1}) %>%
  mutate(sumUnique = Unique.peptides.s1_MCAM_BirA_DMSO_A1 + Unique.peptides.s1_MCAM_BirA_DMSO_A2+
         Unique.peptides.s5_MCAM_BirA_DMSO_B1+ Unique.peptides.s5_MCAM_BirA_DMSO_B2+
         Unique.peptides.s10_MCAM_BirA_DMSO_C1+ Unique.peptides.s10_MCAM_BirA_DMSO_C1) %>%
  filter(sumUnique > 1) %>%
  select(Majority.protein.IDs)

onlyBySite <- proteinGroups %>% filter(Only.identified.by.site == "+") %>% select(Majority.protein.IDs)
allFilteredHumanMQbaq <- formatForMaxQuant(proteinIntensitiesBioNorm %>% filter(!Majority.protein.IDs %in% onlyBySite$Majority.protein.IDs), "iBAQnorm")
allFilteredHumanQCbaq <- filter(allFilteredHumanMQbaq, ((McamBiraA == 0) + (McamBiraB == 0) + (McamBiraC == 0)) < 2) %>%
  filter(Majority.protein.IDs %in% proteinGroups2unique$Majority.protein.IDs) %>%
  filter(Majority.protein.IDs %in% fcMcamNoneBaq$Majority.protein.IDs) %>% arrange(Majority.protein.IDs)

# Save for input to Perseus
write.table(allFilteredHumanQCbaq, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Perseus20230512/Input/20230512_allFilteredHuman20211101BioID_intensityMedianNorm_MQ_QCd_iBAQ_Test.txt", sep = ""),  sep = "\t", row.names = F)
```

Results of t-test in Perseus:
```{r}
perseusAllFilteredQCbaq <- read_delim(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Perseus20230512/Output/20230512_Perseus_allFilteredHuman20211101BioID_intensityMedianNorm_MQ_QCd_iBAQ_Edit.txt", sep = "")) %>%
  rename(qValueMcamLyn = "Student's T-test q-value McamBira_LynBira",
         qValueMcamNes = "Student's T-test q-value McamBira_BiraNes",
         fcMcamLyn = "Student's T-test Difference McamBira_LynBira",
         fcMcamNes = "Student's T-test Difference McamBira_BiraNes",
         pValueMcamLyn = "-Log Student's T-test p-value McamBira_LynBira",
         pValueMcamNes = "-Log Student's T-test p-value McamBira_BiraNes",
         tScoreMcamNes = "Student's T-test Test statistic McamBira_BiraNes") %>%
  mutate(firstID = str_extract(Majority.protein.IDs, "[^;]*")) %>%
  mutate(firstID = ifelse(firstID == "MCAMBirA", "P43121", firstID))


perseusAllFilteredQCbaqS0 <- read_delim(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Perseus20230512/Output/20230512_Perseus_allFilteredHuman20211101BioID_intensityMedianNorm_MQ_QCd_iBAQ_s0-5_Edit.txt", sep = "")) %>%
  rename(qValueMcamLyn = "Student's T-test q-value McamBira_LynBira",
         fcMcamLyn = "Student's T-test Difference McamBira_LynBira",
         pValueMcamLyn = "-Log Student's T-test p-value McamBira_LynBira") %>%
  mutate(firstID = str_extract(Majority.protein.IDs, "[^;]*")) %>%
  mutate(firstID = ifelse(firstID == "MCAMBirA", "P43121", firstID))

identical(perseusAllFilteredQCbaq$Majority.protein.IDs,perseusAllFilteredQCbaqS0$Majority.protein.IDs)
identical(perseusAllFilteredQCbaq$pValueMcamLyn,perseusAllFilteredQCbaqS0$pValueMcamLyn)
identical(perseusAllFilteredQCbaq$qValueMcamLyn,perseusAllFilteredQCbaqS0$qValueMcamLyn) # Should be false
identical(perseusAllFilteredQCbaq$fcMcamLyn,perseusAllFilteredQCbaqS0$fcMcamLyn)
```

Fold-change
```{r}
fcBaq <- proteinIntensitiesBioNorm %>%
  select(Condition, Majority.protein.IDs, Gene.names, iBAQnorm) %>%
  filter(iBAQnorm != 0) %>%
  mutate(iBAQnorm = log2(iBAQnorm))  %>%
  mutate(iBAQnorm = ifelse(is.infinite(iBAQnorm), NA, iBAQnorm)) %>%
  group_by(Condition, Majority.protein.IDs, Gene.names) %>%
  summarize(meanIntensity = mean(iBAQnorm, na.rm = T)) %>%
  ungroup() %>%
  spread(key = Condition, value = meanIntensity) %>%
  dplyr::mutate(fcMcamLyn = McamBira - LynBira,
                fcMcamNes = McamBira - BiraNes,
                avgMcamLyn = (McamBira + LynBira)/2,
                avgMcamNes = (McamBira + BiraNes)/2)
  
fcPerseusBaq <- fcBaq %>%
  filter(Majority.protein.IDs %in% perseusAllFilteredQCbaq$Majority.protein.IDs)
nrow(fcPerseusBaq) == nrow(perseusAllFilteredQCbaq)

test <- merge(perseusAllFilteredQCbaq, fcBaq, by = "Majority.protein.IDs")
all.equal(test$fcMcamLyn.x, test$fcMcamLyn.y)
plot(test$fcMcamLyn.x, test$fcMcamLyn.y) # Looks like some rounding error, but fc is essentially the same as Perseus
plot(test$fcMcamNes.x, test$fcMcamNes.y)
remove(test)
```

```{r}
# SAINT results
reprint17916 <- read.delim(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Reprint20230505/Output/20230503_17916_RenamedPrey_HumanContaminantsOnly_Reprint.tab", sep = ""))
saint17916 <- read.delim(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/Reprint20230505/Output/20230503_17916_RenamedPrey_HumanContaminantsOnly.output", sep = ""))

test <- merge(reprint17916, saint17916, by.x = "PROTID", by.y = "Prey")
plot(test$AvgP, test$MCAM_SP)
remove(test)
## SAINT score from raw SAINT file and REPRINT matrix is not the same (because of "2 best" option). Using SAINT scores from raw SAINT file since I am using the FDR cutoff from this

# Prey in SAINT output converts to all caps. (samples with BirA* and CON__P35908v2).
setdiff(saint17916$Prey, reprintSpcAllRenamedHumanCon$PROTID)
setdiff(reprint17916$PROTID, reprintSpcAllRenamedHumanCon$PROTID)

# Remove common contaminants (human)
sum(duplicated(c(saint17916$Prey, toupper(contaminants$firstIDnew))))
nrow(saint17916 %>% filter(Prey %in% toupper(contaminants$firstIDnew))) # No duplicates

saintFilt <- saint17916 %>%
  filter(!Prey %in% toupper(contaminants$firstIDnew)) %>% # Removed 33
  filter(!Prey %in% c("LYN11BIRA", "BIRANES"))
reprintFilt <- reprint17916 %>% filter(PROTID %in% saintFilt$Prey)
(nrow(saint17916) - nrow(saintFilt)) == (nrow(saint17916 %>% filter(Prey %in% toupper(contaminants$firstIDnew))) + 2) # Number of contaminants + Lyn-BirA* and BirA-NES

# Get "firstID" of all Majority.protein.IDs in proteinGroups file
allFirstID <- proteinGroups %>% dplyr::select(Majority.protein.IDs, Gene.names) %>%
  mutate(firstID = str_extract(Majority.protein.IDs, regex('[^;]*'))) %>%
  mutate(Majority.protein.IDs.New = str_remove_all(Majority.protein.IDs, "CON__ENSEMBL:")) %>%
  mutate(Majority.protein.IDs.New = str_remove_all(Majority.protein.IDs.New, "CON__")) %>%
  mutate(Majority.protein.IDs.New = ifelse(str_detect(Majority.protein.IDs.New, "P04259") & Gene.names != "KRT6B", "CON_P04259", Majority.protein.IDs.New)) %>%
  mutate(Majority.protein.IDs.New = str_remove_all(Majority.protein.IDs.New, "REFSEQ:")) %>%
  mutate(Majority.protein.IDs.New = ifelse(str_detect(Majority.protein.IDs.New, "MCAMBirA"), "P43121", Majority.protein.IDs.New)) %>%
  mutate(firstIDnew = str_extract(Majority.protein.IDs.New, regex('[^;]*')))

# 104 proteins in Perseus analysis were not in SAINT (No SPCs)
length(setdiff(perseusAllFilteredQCbaq$firstID, saintFilt$Prey))
length(setdiff(toupper(perseusAllFilteredQCbaq$firstID), saintFilt$Prey))

missing <- proteinIntensitiesBioNorm %>% 
  filter(Majority.protein.IDs %in% perseusAllFilteredQCbaq$Majority.protein.IDs[perseusAllFilteredQCbaq$firstID %in% setdiff(toupper(perseusAllFilteredQCbaq$firstID), saintFilt$Prey)])
filter(missing, Condition == "McamBira") %>% summarize(sum(spc))

# 417 proteins in SAINT but not Perseus analysis (because of filtering for high confidence identifcations)
length(setdiff(saintFilt$Prey, toupper(perseusAllFilteredQCbaq$firstID)))
setdiff(saintFilt$Prey, toupper(allFirstID$firstIDnew))

# Lyn-BirA* and BirA*-NES were removed during filtering
filter(saint17916, str_detect(Prey, "BIR"))
filter(saintFilt, str_detect(Prey, "BIR"))

setdiff(saint17916$Prey, toupper(allFirstID$firstID))
setdiff(saint17916$Prey, toupper(allFirstID$firstIDnew)) # Making sure that firstIDnew from proteinGroups matches Prey names

setdiff(perseusAllFilteredQCbaq$firstID, allFirstID$firstID) # MCAM
setdiff(perseusAllFilteredQCbaq$firstID, allFirstID$firstIDnew)
```

Figure
```{r}
saintPlot <- merge(saintFilt, reprintFilt %>% dplyr::select(MCAM_FC_A, MCAM_FC_B, PROTID, MCAM_AVG_SPC), by.x = "Prey", by.y = "PROTID") %>%
  mutate(Sig = ifelse(FDR < 0.05, "Yes", "No"))

# 416 significant proteins (after removal of common contaminants)
saintPlot %>% count(Sig)
nrow(saintFilt %>% filter(FDR < 0.05))

sum(is.na(saintFilt$FDR))

# No insignificant SAINT scores above the FDR cutoff
max(saintPlot$AvgP[saintPlot$FDR > 0.05])
min(filter(saintPlot, FDR < 0.05)["AvgP"]) 
```

Figure of SAINT results:
```{r}
ermClr = c("MSN" = "#377eb8", "EZR" = "#4daf4a", "RDX" = "#DFAF37", "MCAM" = "#cf00e2")
sigClr = c("No" = "black", "Yes" = "#9E1A1A")

ggplot() +
  geom_point(data = saintPlot %>% filter(!PreyGene %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")),
             aes(x = log2(MCAM_FC_B), y = as.numeric(AvgP), color = Sig, size = MCAM_AVG_SPC), alpha = 0.2)  +
  geom_point(data = saintPlot %>% filter(PreyGene %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")),
             aes(x = log2(MCAM_FC_B), y = as.numeric(AvgP), size = MCAM_AVG_SPC), fill = "#00B8EA", color = "#007c9e", shape = 21) +
  geom_hline(yintercept = min(filter(saintPlot, FDR < 0.05)["AvgP"])) +
  theme_classic() +
  ylab("Saint Score") +
  xlab("Log2 Fold Change") +
  scale_color_manual(values = sigClr) +
  scale_size_area(breaks = c(1,10,50,100, 1000)) +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 12))
# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/SAINT-Plot_MCAM_Resized_FC_B_LessColorful.svg", sep = ""), width = 4, height = 2, units = "in", dpi = 600)

nrow(saintPlot %>% filter(!PreyGene %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) + nrow(saintPlot %>% filter(PreyGene %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")))
nrow(saintPlot)
anyNA(saintPlot)

ggplot() +
  geom_point(data = saintPlot,
             aes(x = log2(MCAM_FC_B), y = as.numeric(AvgP), color = Sig, size = MCAM_AVG_SPC), alpha = 0.2)  +
  geom_point(data = saintPlot %>% filter(PreyGene %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")),
             aes(x = log2(MCAM_FC_B), y = as.numeric(AvgP), size = MCAM_AVG_SPC, fill = PreyGene ), shape = 21) +
  geom_hline(yintercept = min(filter(saintPlot, FDR < 0.05)["AvgP"])) +
  theme_classic() +
  ylab("Saint Score") +
  xlab("Log2 Fold Change") +
  scale_color_manual(values = sigClr) +
  scale_size_area(breaks = c(1,10,50,100, 1000)) +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 12))
# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/SAINT-Plot_MCAM_Resized_FC_B_ColoredGenes.svg", sep = ""), width = 4, height = 2, units = "in", dpi = 600)

```

Prepare for volcano plot
```{r}
volcanoDataLyn <- merge(perseusAllFilteredQCbaq %>% mutate(firstID = toupper(firstID)), 
                        select(saintPlot, Prey, FDR, Sig), by.x = "firstID", by.y = "Prey", all.x = T, all.y = F) %>%
  mutate(pValueMcamLyn = ifelse((is.nan(LynBiraA)+is.nan(LynBiraB)+is.nan(LynBiraC)) > 1, -.5, pValueMcamLyn)) %>%
  mutate(fcMcamLyn = ifelse(is.nan(fcMcamLyn), 8, fcMcamLyn)) 

# write_csv(volcanoDataLyn, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/volcanoData_NewSaint.csv", sep = ""))

nrow(filter(volcanoDataLyn, is.na(FDR))) # 104
filter(volcanoDataLyn, is.nan(fcMcamLyn))
filter(volcanoDataLyn, fcMcamLyn == 8) # 2 proteins without FC
filter(volcanoDataLyn, pValueMcamLyn == -.5) # 5 proteins without p-value
filter(volcanoDataLyn, pValueMcamLyn == -.5, fcMcamLyn == 8) 
setdiff(perseusAllFilteredQCbaq %>% select(pValueMcamLyn, pValueMcamNes, fcMcamLyn), volcanoDataLyn %>% select(pValueMcamLyn, pValueMcamNes, fcMcamLyn))

filter(volcanoDataLyn, str_detect(firstID, "BIRA"))
sigVolcanoSaint <- volcanoDataLyn %>% filter(Sig == "Yes")

length(setdiff(saintPlot$Prey[saintPlot$Sig == "Yes"], sigVolcanoSaint$firstID)) + nrow(sigVolcanoSaint) #416

```

Volcano plot:
```{r}
fdrSig <- filter(volcanoDataLyn, FDR < 0.05) %>% dplyr::select(Majority.protein.IDs)
nrow(volcanoDataLyn %>% filter(!Majority.protein.IDs %in% fdrSig$Majority.protein.IDs)) + nrow(fdrSig)
nrow(fdrSig) == nrow(sigVolcanoSaint)

ggplot() + 
  geom_point(data = volcanoDataLyn %>% filter(!Majority.protein.IDs %in% fdrSig$Majority.protein.IDs, fcMcamLyn != 8, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), 
             aes(x = fcMcamLyn, y = pValueMcamLyn), alpha = 0.6, size = 1.5)  +
  geom_point(data = volcanoDataLyn %>% filter(Majority.protein.IDs %in% fdrSig$Majority.protein.IDs, fcMcamLyn != 8, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = fcMcamLyn, y = pValueMcamLyn),
             alpha = 0.6, color = "#9E1A1A", size = 1.5) + 
  geom_point(data = volcanoDataLyn %>% filter(Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = fcMcamLyn, y = pValueMcamLyn),
             color = "#00B8EA", size = 2.2) +
  # geom_hline(yintercept = min(volcanoDataLyn$pValueMcamLyn[volcanoDataLyn$qValueMcamLyn < 0.05], na.rm = T)) + 
  theme_classic() + 
    ylab("-log10(p-Value)") +
  xlab("log2(MCAM-BirA*/Lyn11-BirA*)") +
  scale_x_continuous(breaks = seq(-6,6,2), limits = c(-6,6)) +
  theme(text = element_text(size = 18),
        axis.text = element_text(size = 18)) 

# All data was plotted except for 2 proteins with no fold change (missing values for all Lyn-BirA* samples)
nrow(volcanoDataLyn %>% filter(!Majority.protein.IDs %in% fdrSig$Majority.protein.IDs, fcMcamLyn != 8, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) +
  nrow(volcanoDataLyn %>% filter(Majority.protein.IDs %in% fdrSig$Majority.protein.IDs, fcMcamLyn != 8, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) +
  nrow(volcanoDataLyn %>% filter(Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) +
  nrow(volcanoDataLyn %>% filter(fcMcamLyn == 8))

# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/LynVolcanoPlot_WithMCAM_Corrected_FAM129B_LessColor.svg", sep = ""), width = 7, height = 3.7, units = "in", dpi = 600)

ggplot() + 
  geom_point(data = volcanoDataLyn %>% filter(!Majority.protein.IDs %in% fdrSig$Majority.protein.IDs, fcMcamLyn != 8, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), 
             aes(x = fcMcamLyn, y = pValueMcamLyn), alpha = 0.6, size = 1.5)  +
  geom_point(data = volcanoDataLyn %>% filter(Majority.protein.IDs %in% fdrSig$Majority.protein.IDs, fcMcamLyn != 8, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = fcMcamLyn, y = pValueMcamLyn),
             alpha = 0.6, color = "#9E1A1A", size = 1.5) + 
  geom_point(data = volcanoDataLyn %>% filter(Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = fcMcamLyn, y = pValueMcamLyn, color = Gene.names), size = 2.2) +
  # geom_hline(yintercept = min(volcanoDataLyn$pValueMcamLyn[volcanoDataLyn$qValueMcamLyn < 0.05], na.rm = T)) + 
  theme_classic() + 
    ylab("-log10(p-Value)") +
  xlab("log2(MCAM-BirA*/Lyn11-BirA*)") +
  scale_x_continuous(breaks = seq(-6,6,2), limits = c(-6,6)) +
  theme(text = element_text(size = 18),
        axis.text = element_text(size = 18)) 
# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/LynVolcanoPlot_WithMCAM_Corrected_FAM129B_ColoredGenes.svg", sep = ""), width = 7, height = 3.7, units = "in", dpi = 600)
```
MA plot for results
```{r}
# Significant proteins
sigPerseus <- perseusAllFilteredQCbaq %>% filter(qValueMcamLyn < 0.05)
sigPerseusS0 <- perseusAllFilteredQCbaqS0 %>% filter(qValueMcamLyn < 0.05)

allPerseusMaj <- union(sigPerseus$Majority.protein.IDs, sigPerseusS0$Majority.protein.IDs)

perseusAllFilteredQCbaq %>% filter(Majority.protein.IDs %in% allPerseusMaj) %>%
  filter(!firstID %in% saintPlot$Prey) 
perseusAllFilteredQCbaq %>% filter(Majority.protein.IDs %in% allPerseusMaj) %>% 
  filter(!firstID %in% saintPlot$Prey, fcMcamLyn < 0) # 26 proteins with significant negative fold-change were not in the SAINT analysiss

perseusAllFilteredQCbaq %>% filter(Majority.protein.IDs %in% allPerseusMaj) %>% 
  filter(!firstID %in% saintPlot$Prey, fcMcamLyn > 0) # None of the proteins with positive enrichment are excluded from SAINT analysis

ggplot() +
  geom_point(data = fcPerseusBaq %>% filter(!Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"), !is.na(fcPerseusBaq$fcMcamLyn)), aes(x = avgMcamLyn, y = fcMcamLyn), alpha = 0.4, size = 1.5) +
  geom_point(data = fcPerseusBaq %>% filter(Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"), !is.na(fcPerseusBaq$fcMcamLyn)), aes(x = avgMcamLyn, y = fcMcamLyn), color = "#e66101", size = 1.8, alpha = 0.7) +
  geom_point(data = fcPerseusBaq %>% filter(Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = avgMcamLyn, y = fcMcamLyn), color = "#00B8EA", size = 2) +
  theme_classic() +
  geom_hline(yintercept = 0) +
  ylim(-6,6) +
  ylab("log2(MCAM-BirA*/Lyn11-BirA*)") +
  xlab("Average Normalized iBAQ") +
  theme(text = element_text(size = 18))

nrow(fcPerseusBaq %>% filter(!Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) +
  nrow(fcPerseusBaq %>% filter(Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) +
  nrow(fcPerseusBaq %>% filter(Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")))
nrow(fcPerseusBaq %>% filter(!Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"), !is.na(fcPerseusBaq$fcMcamLyn))) +
  nrow(fcPerseusBaq %>% filter(Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"), !is.na(fcPerseusBaq$fcMcamLyn))) +
  nrow(fcPerseusBaq %>% filter(Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")))
sum(is.na(fcPerseusBaq$fcMcamLyn))
sum(is.na(fcPerseusBaq$avgMcamLyn))

nrow(fcPerseusBaq %>% filter(!Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) + nrow(fcPerseusBaq %>% filter(Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B"))) + 5

# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/MAplot_Results.svg", sep = ""), width = 6, height = 3.7, units = "in", dpi = 600)

ggplot() +
  geom_point(data = fcPerseusBaq %>% filter(!Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = avgMcamLyn, y = fcMcamLyn), alpha = 0.4, size = 1.5) +
  geom_point(data = fcPerseusBaq %>% filter(Majority.protein.IDs %in% allPerseusMaj, !Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = avgMcamLyn, y = fcMcamLyn), color = "#e66101", size = 1.8, alpha = 0.7) +
  geom_point(data = fcPerseusBaq %>% filter(Gene.names %in% c("MSN", "RDX", "EZR", "MCAM", "FAM129B")), aes(x = avgMcamLyn, y = fcMcamLyn, color = Gene.names), size = 2) +
  theme_classic() +
  geom_hline(yintercept = 0) +
  ylim(-6,6) +
  ylab("log2(MCAM-BirA*/Lyn11-BirA*)") +
  xlab("Average Normalized iBAQ") +
  theme(text = element_text(size = 18))
# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/MAplot_Results_ColoredGenes.svg", sep = ""), width = 6, height = 3.7, units = "in", dpi = 600)
```

MA and volcano plot for supplemental
```{r}
# Proteins that were significant with one or both s0 settings (0 or 0.5)
bothPerseusMaj <- intersect(sigPerseus$Majority.protein.IDs, sigPerseusS0$Majority.protein.IDs)
onlyPerseusMaj <- setdiff(sigPerseus$Majority.protein.IDs, sigPerseusS0$Majority.protein.IDs)
onlyS0Maj <- setdiff(sigPerseusS0$Majority.protein.IDs, sigPerseus$Majority.protein.IDs)

(length(bothPerseusMaj) + length(onlyS0Maj) + length(onlyPerseusMaj)) == length(allPerseusMaj)

ggplot() +
  geom_point(data = fcPerseusBaq %>% filter(!Majority.protein.IDs %in% allPerseusMaj, !is.na(fcMcamLyn)), aes(x = avgMcamLyn, y = fcMcamLyn), alpha = 0.3, size = 1.5) +
  geom_point(data = fcPerseusBaq %>% filter(Majority.protein.IDs %in% bothPerseusMaj), aes(x = avgMcamLyn, y = fcMcamLyn), alpha = 0.9, color = "#e66101", size = 2) +
  geom_point(data = fcPerseusBaq %>% filter(Majority.protein.IDs %in% onlyPerseusMaj), aes(x = avgMcamLyn, y = fcMcamLyn), alpha = 0.9, color = "#e8ba28", size = 2) +
  geom_point(data = fcPerseusBaq %>% filter(Majority.protein.IDs %in% onlyS0Maj), aes(x = avgMcamLyn, y = fcMcamLyn),alpha = 0.9, color = "#8a00c2", size = 2) +
  theme_classic() +
  geom_hline(yintercept = 0) +
  ylim(-6,6) +
  ylab("log2(MCAM-BirA*/Lyn11-BirA*)") +
  xlab("Average Normalized iBAQ") +
  theme(text = element_text(size = 18))
# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/MAplot_Significance.svg", sep = ""), width = 6, height = 3.7, units = "in", dpi = 600)

nrow(fcPerseusBaq %>% filter(!Majority.protein.IDs %in% allPerseusMaj, !is.na(fcMcamLyn))) + 
  nrow(fcPerseusBaq %>% filter(Majority.protein.IDs %in% bothPerseusMaj)) + 
  nrow(fcPerseusBaq %>% filter(Majority.protein.IDs %in% onlyPerseusMaj)) + 
  nrow(fcPerseusBaq %>% filter(Majority.protein.IDs %in% onlyS0Maj))

ggplot(data = volcanoDataLyn, aes(x = fcMcamLyn, y = pValueMcamLyn)) + 
  geom_point(data = volcanoDataLyn %>% filter(!Majority.protein.IDs %in% allPerseusMaj, fcMcamLyn != 8), aes(x = fcMcamLyn, y = pValueMcamLyn), alpha = 0.3, size = 1.5)  +
  geom_point(data = volcanoDataLyn %>% filter(Majority.protein.IDs %in% bothPerseusMaj, fcMcamLyn != 8), alpha = 0.9, color ="#e66101", size = 2) + 
  geom_point(data = volcanoDataLyn %>% filter(Majority.protein.IDs %in% onlyPerseusMaj, fcMcamLyn != 8), alpha = 0.9, color ="#e8ba28", size = 2) + 
  geom_point(data = volcanoDataLyn %>% filter(Majority.protein.IDs %in% onlyS0Maj, fcMcamLyn != 8), alpha = 0.9, color ="#8a00c2", size = 2) + 
  # geom_hline(yintercept = min(volcanoDataLyn$pValueMcamLyn[volcanoDataLyn$qValueMcamLyn < 0.05], na.rm = T)) + 
  theme_classic() + 
    ylab("-log10(p-Value)") +
  xlab("log2(MCAM-BirA*/Lyn11-BirA*)") +
  scale_x_continuous(breaks = seq(-6,6,2), limits = c(-6,6)) +
  theme(text = element_text(size = 18),
        axis.text = element_text(size = 18)) 

nrow(volcanoDataLyn %>% filter(!Majority.protein.IDs %in% allPerseusMaj, fcMcamLyn != 8)) + nrow(volcanoDataLyn %>% filter(Majority.protein.IDs %in% bothPerseusMaj, fcMcamLyn != 8)) +
  nrow(volcanoDataLyn %>% filter(Majority.protein.IDs %in% onlyPerseusMaj, fcMcamLyn != 8)) + nrow(volcanoDataLyn %>% filter(Majority.protein.IDs %in% onlyS0Maj, fcMcamLyn != 8)) +
  nrow(volcanoDataLyn %>% filter(fcMcamLyn == 8))

# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/LynVolcanoPlot_WithMCAM_Corrected_Significance.svg", sep = ""), width = 7, height = 3.7, units = "in", dpi = 600)
```

Significant genes with positive fold-change:
```{r}
hitPerseus <- sigPerseus %>% filter(fcMcamLyn > 0)
hitPerseusS0 <- sigPerseusS0 %>% filter(fcMcamLyn > 0)
hitPM <- union(hitPerseusS0$Majority.protein.IDs, hitPerseus$Majority.protein.IDs)

hitBaq <- perseusAllFilteredQCbaq %>%
  filter(Majority.protein.IDs %in% allPerseusMaj, fcMcamLyn > 0) %>%
  dplyr::mutate(Significant = ifelse(Majority.protein.IDs %in% bothPerseusMaj, "Both", NA)) %>%
  dplyr::mutate(Significant = ifelse(Majority.protein.IDs %in% onlyPerseusMaj, "s0 = 0", Significant)) %>%
  dplyr::mutate(Significant = ifelse(Majority.protein.IDs %in% onlyS0Maj, "s0 = 0.5", Significant),
                SigSaint = ifelse(Majority.protein.IDs %in% fdrSig$Majority.protein.IDs, "Yes", "No")) %>%
  merge(fcPerseusBaq %>% select(avgMcamLyn, Majority.protein.IDs), by = "Majority.protein.IDs")

setdiff(hitBaq$Majority.protein.IDs, hitPM)
hitSaintAndPerseus <- intersect(hitPM, fdrSig$Majority.protein.IDs)
setdiff(hitSaintAndPerseus, hitBaq$Majority.protein.IDs[hitBaq$SigSaint == "Yes"])
setdiff(hitBaq$Majority.protein.IDs[hitBaq$SigSaint == "Yes"], hitSaintAndPerseus)

hitBaq # 30 proteins with significant positive fold changes
# write_csv(hitBaq, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/perseus_SignificantResults.csv", sep = ""))

# All positively enriched significant proteins in SAINT (26 of the proteins with significant negative enrichment were not in SAINT)
perseusAllFilteredQCbaq %>% filter(Majority.protein.IDs %in% hitPM) %>%
  filter(!firstID %in% saintFilt$Prey)

noFC <- filter(fcPerseusBaq, is.na(fcMcamLyn))
```

Bar graph for ERM proteins
```{r}
bar <- function(intensities, genes, title){
  meanIntensities <- intensities %>% 
    group_by(Condition, Protein.IDs, Gene.names) %>%
    summarize(meanNorm = mean(iBAQnorm, na.rm = T),
              sdNorm = sd(iBAQnorm, na.rm = T),
              mean = mean(iBAQ, na.rm = T),
              sd = sd(iBAQ, na.rm = T),
              seNorm = sd(iBAQnorm, na.rm = T)/length(iBAQnorm),
              se = sd(iBAQ, na.rm = T)/length(iBAQ)) %>%
    ungroup() 
  
  condClr <- c("BiraNes" = "#fb8072", "LynBira" = "#80b1d3", "McamBira" = "#fdb462")
  
  print(ggplot(meanIntensities %>% filter(Gene.names %in% genes), aes(x = Gene.names, y = mean, fill = Condition)) + geom_col(position = "dodge") +
    geom_point(data = intensities %>% filter(Gene.names %in% genes), aes(x = Gene.names, y = iBAQ, fill = Condition), position = position_jitterdodge(jitter.height = 0, jitter.width = 0.05), alpha = .7, shape = 21) + ggtitle("Raw") +
    geom_errorbar(data = meanIntensities %>% filter(Gene.names %in% genes), aes(ymin = mean-sd, ymax = mean+sd),
                  position = position_dodge(width=0.9), alpha = 0.7, width = 0.4) +
    theme_classic() +
    theme(text = element_text(size = 18),
          axis.text = element_text(size = 18),
          legend.text = element_text(size = 14)) +
      scale_fill_manual(values = condClr) +
      ylab("Raw iBAQ"))
  
  print(ggplot(meanIntensities %>% filter(Gene.names %in% genes), aes(x = Gene.names, y = meanNorm, fill = Condition)) + geom_col(position = "dodge") +
    geom_point(data = intensities %>% filter(Gene.names %in% genes), aes(x = Gene.names, y = iBAQnorm, fill = Condition), position = position_jitterdodge(jitter.height = 0, jitter.width = 0.2, dodge.width = .9), alpha = .7, size = 2) + ggtitle(title) +
    geom_errorbar(data = meanIntensities %>% filter(Gene.names %in% genes), aes(ymin = meanNorm-sdNorm, ymax = meanNorm+sdNorm),
                  position = position_dodge(width=0.9), alpha = 0.7, width = 0.4) +
      theme_classic() +
    theme(text = element_text(size = 18),
          axis.text = element_text(size = 18),
          legend.text = element_text(size = 14)) +
      scale_fill_manual(values = condClr) +
      ylab("Normalized iBAQ"))
  
  
  for(val in 1:length(genes)){
    
    print(genes[val])
    print("Norm iBAQ")
    print(t.test(filter(intensities, Gene.names == genes[val], Condition == "McamBira") %>% select(iBAQnorm) %>% mutate_all(log2),
           filter(intensities, Gene.names == genes[val], Condition == "LynBira") %>% select(iBAQnorm) %>% mutate_all(log2)), alternative = "greater")
  }
}

bar(proteinIntensitiesBioNorm %>%
      filter(Condition != "None", Condition != "McamBiraROCKi") %>%
      filter(Gene.names %in% c("MSN", "RDX", "EZR")) %>%
      mutate(Gene.names = factor(Gene.names, levels = c("MSN", "EZR", "RDX"))), c("MSN", "RDX", "EZR"), "Normalized iBAQ")

# ggsave(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/FiguresForPaper/ERM_NormalizediBAQ.svg",sep = ""),
   # width = 5, height = 3.5, units = "in", dpi = 600)
```

P-values based on FDR adjusted T-test in Perseus (used for significance of bar graphs)
```{r}
filter(perseusAllFilteredQCbaq, Gene.names %in% (c("MSN", "RDX", "EZR"))) %>%
  select(Gene.names, all_of(contains("qValue")), all_of(contains("pValue"))) %>%
  arrange(qValueMcamLyn)
```

Significantly enriched SAINT genes for GSE:
```{r}
sigSaint <- saintFilt %>% filter(FDR < 0.05) %>%
  dplyr::select(Prey, PreyGene) %>% 
  merge(allFirstID %>% dplyr::select(Majority.protein.IDs, Gene.names, firstIDnew) %>%
          mutate(firstIDnew = toupper(firstIDnew)), by.x = "Prey", by.y = "firstIDnew")

# write.csv(sigSaint, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/GSE/Paper/significant_NewSaint_Test.csv", sep = ""))
```

Combine SAINT and REPRINT for supplemental:
```{r}
supp <- merge(saintFilt, reprintFilt %>% dplyr::select(PROTID, MCAM_AVG_SPC, MCAM_FC_A, MCAM_FC_B), by.x = "Prey", by.y = "PROTID")
all.equal(saintFilt %>% arrange(Prey), supp %>% select(colnames(saintFilt)) %>% arrange(Prey))
all.equal(reprintFilt %>% arrange(PROTID) %>% select(any_of(colnames(supp))), supp %>% arrange(Prey) %>% select(any_of(colnames(reprintFilt))))
nrow(supp) == nrow(saintFilt)
anyNA(supp)

write_csv(supp, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/SupplementalSaintData.csv", sep = ""))
test <- read.csv(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/SupplementalSaintData_Test.csv", sep = "")) 

all.equal(saintFilt %>% arrange(Prey), test %>% select(colnames(saint17916)))
```
```{r}
# Supplemental data from evidence file
evidenceCols <- read.csv(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/evidenceColnames_supplemental.csv", sep = ""))

suppEvidence <- evidence2 %>%
  filter(Reverse != "+") %>%
  dplyr::select(all_of(evidenceCols$Selected[1:31])) %>%
  rename(Andromeda.score = Score)
write_csv(suppEvidence, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/evidenceSupplemental.csv", sep = ""))

# Supplemental data: protein quantification for technical replicates
annotation2 <- annotation %>% filter(!str_detect(ProteinGroups, "s4"), !str_detect(ProteinGroups, "s9"))
suppPgIntensity <- proteinsAll2 %>% 
  dplyr::select(Majority.protein.IDs, intensity, Raw.file, Reverse) %>%
  filter(Reverse != "+") %>%
  merge(proteinGroups %>% dplyr::select(Majority.protein.IDs, iBAQ.peptides), by = "Majority.protein.IDs") %>%
  merge(annotation2 %>% dplyr::select(ProteinGroups, Raw.file), by = "Raw.file") %>%
  dplyr::mutate(iBAQ = intensity/iBAQ.peptides) %>%
  dplyr::select(-Raw.file, -intensity) %>%
  spread(key = ProteinGroups, value = iBAQ, fill = 0) %>%
  rename_with(.fn = function(.x){paste0(.x, "_iBAQ")}, .cols = annotation2$ProteinGroups)

suppPgSpc <- proteinsAll2 %>% 
  dplyr::select(Majority.protein.IDs, spc, Raw.file, Reverse) %>%
  filter(Reverse != "+") %>%
  merge(proteinGroups %>% dplyr::select(Majority.protein.IDs), by = "Majority.protein.IDs") %>%
  merge(annotation2 %>% dplyr::select(ProteinGroups, Raw.file), by = "Raw.file") %>%
  dplyr::select(-Raw.file) %>%
  spread(key = ProteinGroups, value = spc, fill = 0) %>%
  rename_with(.fn = function(.x){paste0(.x, "_MS.MS.counts")}, .cols = annotation2$ProteinGroups)

pgCols <- read.csv(paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/colnamesPg_Supplemental.csv", sep = ""))

suppPg <- merge(suppPgIntensity %>% dplyr::select(-Reverse), suppPgSpc %>% dplyr::select(-Reverse), by = "Majority.protein.IDs") %>%
  merge(proteinGroups %>% dplyr::select(all_of(pgCols$Selected1[1:75])), by = "Majority.protein.IDs") %>%
  dplyr::select(all_of(pgCols$Selected2[1:119]))

# Check
length(colnames(suppPg))
filter(suppPg, Majority.protein.IDs %in% proteinGroups$Majority.protein.IDs[proteinGroups$Reverse == "+"])
anyNA(suppPg)

write_csv(suppPg, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/proteinGroupsSupplemental.csv", sep = ""))

# Perseus supplemental
suppPerseus <- allFilteredHumanQCbaq %>%
  merge(perseusAllFilteredQCbaq %>% 
          dplyr::select(pValueMcamLyn, pValueMcamNes, qValueMcamLyn, qValueMcamNes, Majority.protein.IDs) %>%
          dplyr::mutate(pValueMcamLyn = 10^(-pValueMcamLyn)) %>%
          dplyr::mutate(pValueMcamNes = 10^(-pValueMcamNes)) %>%
          rename(pValue.Mcam.Vs.LynBira = pValueMcamLyn,
                 pValue.Mcam.Vs.BiraNes = pValueMcamNes,
                 qValue.Mcam.Vs.LynBira = qValueMcamLyn,
                 qValue.Mcam.Vs.BiraNes = qValueMcamNes), by = "Majority.protein.IDs") %>%
  merge(perseusAllFilteredQCbaqS0 %>% dplyr::select(Majority.protein.IDs, qValueMcamLyn) %>%
          rename(qValue.Mcam.Vs.LynBirA.s0.5 = qValueMcamLyn), by = "Majority.protein.IDs") %>%
  merge(fcPerseusBaq %>% dplyr::select(Majority.protein.IDs, fcMcamLyn, fcMcamNes) %>%
          rename(Foldchange.Mcam.Vs.LynBira = fcMcamLyn,
                 Foldchange.Mcam.Vs.BiraNes = fcMcamNes), by = "Majority.protein.IDs")

# Check values were preserved
plot(perseusAllFilteredQCbaq$pValueMcamLyn, -log10(suppPerseus$pValue.Mcam.Vs.LynBira))
plot(perseusAllFilteredQCbaq$pValueMcamNes, -log10(suppPerseus$pValue.Mcam.Vs.BiraNes))
all.equal(suppPerseus %>% dplyr::select(any_of(colnames(allFilteredHumanQCbaq))), allFilteredHumanQCbaq %>% dplyr::select(any_of(colnames(suppPerseus))) %>% dplyr::select(any_of(colnames(allFilteredHumanQCbaq))))
identical(suppPerseus$qValue.Mcam.Vs.LynBira, perseusAllFilteredQCbaq$qValueMcamLyn)
identical(suppPerseus$qValue.Mcam.Vs.BiraNes, perseusAllFilteredQCbaq$qValueMcamNes)
identical(suppPerseus$qValue.Mcam.Vs.LynBirA.s0.5, perseusAllFilteredQCbaqS0$qValueMcamLyn)
identical(suppPerseus$Foldchange.Mcam.Vs.LynBira, fcPerseusBaq$fcMcamLyn)
identical(suppPerseus$Foldchange.Mcam.Vs.BiraNes, fcPerseusBaq$fcMcamNes)

write_csv(suppPerseus, paste(dirPath, "MassSpecAnalysis/Paper_FinalAnalyses/perseusSupplemental.csv", sep = ""))
```

